---
title: "B_merge"
---

# LEALCO-EEG: analyse data *from test task*

# Information

### Goal

### Inputs

The output file is a large .csv table containing the entire data of the file in a long format. It puts together the PsychoPy input files, the demographics, the VOT files as well as the relevant information from the debriefing questionnaire.

### Output

# Load packages

```{r}
#install.packages("factoextra")
#install.packages("cocor")
```

```{r}
library(dplyr)
library(tidyverse)
library(lme4)
library(buildmer)
library(emmeans)
library(lmerTest)
library(gridExtra)
library(sjPlot)
library(factoextra)
library(chron)
library(cocor)
source("R/utils.R")
```

# Set some custom settings

```{r}

#theme_set(theme_gray())
theme_set(theme_bw())
#pal1 = c("#2d8fd5", "#87cdff")
pal1 = c("#F5793A", "#4f5dab")
pal2 = c("#138471", "#70beb1")
```

# Read files

Read files

```{r}
# ================ read files
data <- read.csv('data/LEALCO-EEG_test_merged_data_eeg_all.csv')
demo <- read.csv('data/demographic/data_LEALCO-EEGdem_2025-06-04_12-52.csv',  sep = ";", fileEncoding = "Latin1", check.names = F)
offsets <- read.csv('data/LEALCO-EEG_test_merged_data_offsets.csv')
```

Make certain variables into factors

```{r}
# merge offsets data
offsets <- offsets %>%
  select(target_stimID, offset, subjID, block)
data <- left_join(data, offsets, by=c('subjID', 'block', 'target_stimID'))

      
# transform some variables
data$subjID <- as_factor(data$subjID)
data$partner_order <- as_factor(data$partner_order)
data$key_trained <- as_factor(data$key_trained)
data$key_untrained <- as_factor(data$key_untrained)
data$block <- as_factor(data$block)
data$partner <- as_factor(data$partner)
data$class <- as_factor(data$class)
data$partner_type <- as_factor(data$partner_type)
data$SUBTLEX_frequency_log_cat <- as_factor(data$SUBTLEX_frequency_log_cat)
data$error <- as_factor(data$error)
data$target_label <- as_factor(data$target_label)
data$Gender <- as_factor(data$Gender)
data$Händigkeit <- as_factor(data$Händigkeit)
data$VOT <- as.numeric(data$VOT)
data$correct <- as.numeric(data$correct)

# reorder some levels
data$partner_type <- relevel(data$partner_type, "same")

# change name for some variable levels
demo$Gender[demo$Gender == 1] <- 'male' 
demo$Gender[demo$Gender == 2] <- 'female' 
demo$Gender[demo$Gender == 4] <- 'other' 
demo$Gender[demo$Gender == 5] <- 'no_answer' 

```

```{r}
p <- data %>%
  ggplot( aes(x=offset, fill=partner_type)) +
    geom_histogram( color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=pal1) +
    facet_wrap(~partner_order)
p

```

For each trial, create new variable containing the perceived quality of teamwork, depending on the current partner (this just takes the correct value from the debriefing questionnaire, depending on which partner the trial took place with)

```{r}
# 
data$team  <- ifelse(data$partner == 'A', data$T101, data$T201)
```

# Preliminary data sanity checks

## (1) Check general error pattern

Here, the general error distribution (regardless of experimental condition) is assessed by subject. This can potentially constitute the basis for data exclusion.

| Code    | Meaning                                     |
|---------|---------------------------------------------|
| correct | said exactly what they were expected to say |
| 1       | compounded                                  |
| 2       | semantically related                        |
| 3       | phonologically related                      |
| 4       | unrelated                                   |
| 5       | misarticulation                             |
| 6       | other                                       |
| 7       | visual                                      |
| 8       | audio recording error                       |
| 9       | no response                                 |

: Table 1: Key for interpreting the "Error"" variable

```{r}
# plot accuracy counts by subject
pdf("output_figures/LEALCO-EEG_raw screening.pdf")
p <- ggplot(data, aes(x=error, fill=error)) + 
  geom_bar() +
  facet_wrap(~subjID)
p
dev.off()
p

# count how many trials of each type
data %>% count(error) 

```

## (2) Check general RT pattern

Let's screen for anomalous RTs in the data files, which could have originated from inaccuracies in data reprocessing. It appears that no anomalies are (any longer) present in the data.

```{r}

# overall density plot
plot(density(data$VOT, na.rm = TRUE))

# zooming into the left part of the histogramm to spot anomalous VOTs (<400 ms), and export them.
hist(data$VOT, xlim=c(0, 1000), breaks = 1000)
dummy <- data[data$VOT < 500,]
write.csv(dummy, 'data/LEALCO-EEG_test_anomalous_RTs.csv', row.names=FALSE, fileEncoding = "UTF-8")

# Look for NA values and export them.
dummy <- data[is.na(data$VOT),]
write.csv(dummy, 'data/LEALCO-EEG_test_anomalousNA_RTs.csv', row.names=FALSE, fileEncoding = "UTF-8")

# histogramm fo ronly correct responses
hist(data$VOT[data$correct == 1], xlim=c(0, 1000), breaks = 1000)
plot(density(data$VOT[data$correct == 1], na.rm = TRUE))
```

## (3) Transform non-normal variables

After trying several normalization approaches, it appears that the **inverse** **normalization** is most appropriatel.

```{r}

# plot native VOTs
hist(data$VOT, breaks=500)

# plot log10 notmalized VOTs
data$VOTlog10 <- log10(data$VOT)
hist(data$VOTlog10, breaks=500)

# plot inverse normalized VOTs
data$VOTinv <- 1/data$VOT
hist(data$VOTinv[data$correct==1], breaks=500)

# plot square root normalized VOTs
data$VOTsqrt <- sqrt(data$VOT)
hist(data$VOTsqrt, breaks=500)
```

## (4) Are there anomalous subjects?

Calculate descriptive across collapsed conditions. Note that no trials/subjects are excluded.

```{r}

# descritpives of accuracy: within-subjects
summary_acc_wSubj <- data %>%
  group_by(subjID) %>%
  summarise(mean_ACC = mean(correct), sd=sd(correct), sem=(sd(correct)/sqrt((length(correct)))))

# descritpives of accuracy: between-subjects
summary_acc_bSubj <- summary_acc_wSubj %>%
  summarise(grand_mean_ACC = mean(mean_ACC), sd=sd(mean_ACC), sem=(sd(mean_ACC)/sqrt((length(mean_ACC)))))

# descritpives of vot: within-subjects
summary_vot_wSubj <- data %>%
  filter(correct == 1) %>%
  group_by(subjID) %>%
  summarise(mean_VOT = mean(VOT), sd=sd(VOT), sem=(sd(VOT)/sqrt((length(VOT)))))

# descritpives of vot: between-subjects
summary_vot_bSubj <- summary_vot_wSubj %>%
  summarise(grand_mean_VOT = mean(mean_VOT), sd=sd(mean_VOT), sem=(sd(mean_VOT)/sqrt((length(mean_VOT)))))
```

# == Trained Trials ==

## Subject exclusion

Select trained trials, with a focus on those that are valid, i.e. where no recording error occurred. We therefore exclude all trials coded as: (5) misarticulation, (6) other, (7) visual, (8) audio recording error (9) no response.

```{r}
data_trained <- data %>%
  filter(class == 'test item') %>%
  filter(error %in% c('correct', '1', '2', '3', '4'))
```

Determine if any subjects need to be excluded based on data distribution for **accuracy** (collapsing all test conditions).

```{r}

# aggregate within subject
data_trained_sum_wSubj <- data_trained %>%
  group_by(subjID) %>%
  summarise(mean = mean(correct), sem=(sd(correct)/sqrt((length(correct)))), sd=sd(correct))

# aggregate between subjects
data_trained_sum_bSubj <- data_trained_sum_wSubj %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# calculate SD intervals
plus2SD = data_trained_sum_bSubj$grandMean + data_trained_sum_bSubj$sd * 2
minus2SD = data_trained_sum_bSubj$grandMean - data_trained_sum_bSubj$sd * 2
plus25SD = data_trained_sum_bSubj$grandMean + data_trained_sum_bSubj$sd * 2.5
minus25SD = data_trained_sum_bSubj$grandMean - data_trained_sum_bSubj$sd * 2.5
plus3SD = data_trained_sum_bSubj$grandMean + data_trained_sum_bSubj$sd * 3
minus3SD = data_trained_sum_bSubj$grandMean - data_trained_sum_bSubj$sd * 3

# plot
pdf("output_figures/LEALCO-EEG_acc_outliers.pdf")
p <- ggplot(data_trained_sum_wSubj, aes(x=mean)) +
  geom_dotplot() +
  geom_density(alpha=.2, fill="black") +
  geom_vline(aes(xintercept=data_trained_sum_bSubj$grandMean)) +
  geom_vline(aes(xintercept=plus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus3SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus3SD), linetype="dashed") +
  annotate("text", x=plus2SD, y=3, label="+2SD", angle = 30) +
  annotate("text", x=minus2SD, y=3, label="-2SD", angle = 30) +
  annotate("text", x=plus25SD, y=3, label="+2.5SD", angle = 30) +
  annotate("text", x=minus25SD, y=3, label="-2.5SD", angle = 30) +
  annotate("text", x=plus3SD, y=3, label="+3SD", angle = 30) +
  annotate("text", x=minus3SD, y=3, label="-3SD", angle = 30) +
  annotate("text", x=data_trained_sum_bSubj$grandMean, y=3, label="mean", angle = 30) +
  xlim(0,1) +
 ggtitle("Subject outliers based on accuracy")
dev.off()
p

# select outliers on the basis of +/-2SD
data_trained_sum_wSubj[data_trained_sum_wSubj$mean < minus2SD |
                       data_trained_sum_wSubj$mean > plus2SD, ]

# select outliers on the basis of +/-2.5SD
data_trained_sum_wSubj[data_trained_sum_wSubj$mean < minus25SD |
                       data_trained_sum_wSubj$mean > plus25SD, ]

# select outliers on the basis of +/-3SD
data_trained_sum_wSubj[data_trained_sum_wSubj$mean < minus3SD |
                       data_trained_sum_wSubj$mean > plus3SD, ]
```

Do same thing with **naming latencies**.

```{r}

# aggregate within subject
data_trained_sum_wSubj_vot <- data_trained %>%
  group_by(subjID) %>%
  summarise(mean = mean(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), sd=sd(VOT))

# aggregate between subjects
data_trained_sum_bSubj_vot <- data_trained_sum_wSubj_vot %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# calculate SD intervals
plus2SD = data_trained_sum_bSubj_vot$grandMean + data_trained_sum_bSubj_vot$sd * 2
minus2SD = data_trained_sum_bSubj_vot$grandMean - data_trained_sum_bSubj_vot$sd * 2
plus25SD = data_trained_sum_bSubj_vot$grandMean + data_trained_sum_bSubj_vot$sd * 2.5
minus25SD = data_trained_sum_bSubj_vot$grandMean - data_trained_sum_bSubj_vot$sd * 2.5
plus3SD = data_trained_sum_bSubj_vot$grandMean + data_trained_sum_bSubj_vot$sd * 3
minus3SD = data_trained_sum_bSubj_vot$grandMean - data_trained_sum_bSubj_vot$sd * 3

# plot
pdf("output_figures/LEALCO-EEG_vot_outliers.pdf")
p2 <- ggplot(data_trained_sum_wSubj_vot, aes(x=mean)) +
  geom_dotplot() +
  geom_density(alpha=.2, fill="black") +
  geom_vline(aes(xintercept=data_trained_sum_bSubj_vot$grandMean)) +
  geom_vline(aes(xintercept=plus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus3SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus3SD), linetype="dashed") +
  annotate("text", x=plus2SD, y=3, label="+2SD", angle = 30) +
  annotate("text", x=minus2SD, y=3, label="-2SD", angle = 30) +
  annotate("text", x=plus25SD, y=3, label="+2.5SD", angle = 30) +
  annotate("text", x=minus25SD, y=3, label="-2.5SD", angle = 30) +
  annotate("text", x=plus3SD, y=3, label="+3SD", angle = 30) +
  annotate("text", x=minus3SD, y=3, label="-3SD", angle = 30) +
  annotate("text", x=data_trained_sum_bSubj_vot$grandMean, y=3, label="mean", angle = 30) +
  xlim(0,NA) 
  ggtitle("Subject outliers based on naming latency (native)")
dev.off()
p2

# select subjects with daata beyond +/-2SDs 
data_trained_sum_wSubj_vot[data_trained_sum_wSubj_vot$mean < minus2SD |
                       data_trained_sum_wSubj_vot$mean > plus2SD, ]

# select subjects with daata beyond +/-2.5SDs 
data_trained_sum_wSubj_vot[data_trained_sum_wSubj_vot$mean < minus25SD |
                       data_trained_sum_wSubj_vot$mean > plus25SD, ]

# select subjects with daata beyond +/-3SDs 
data_trained_sum_wSubj_vot[data_trained_sum_wSubj_vot$mean < minus3SD |
                       data_trained_sum_wSubj_vot$mean > plus3SD, ]
```

Do the same with **inverted naming latencies**.

```{r}

# aggregate within subject
data_trained_sum_wSubj_votINV <- data_trained %>%
  group_by(subjID) %>%
  summarise(mean = mean(VOTinv), sem=(sd(VOTinv)/sqrt((length(VOTinv)))), sd=sd(VOTinv))

# aggregate between subjects
data_trained_sum_bSubj_votINV <- data_trained_sum_wSubj_votINV %>%
  summarise(grandMean = mean(mean), sem=(sd(mean)/sqrt((length(mean)))), sd=sd(mean))

# calculate SD intervals
plus2SD = data_trained_sum_bSubj_votINV$grandMean + data_trained_sum_bSubj_votINV$sd * 2
minus2SD = data_trained_sum_bSubj_votINV$grandMean - data_trained_sum_bSubj_votINV$sd * 2
plus25SD = data_trained_sum_bSubj_votINV$grandMean + data_trained_sum_bSubj_votINV$sd * 2.5
minus25SD = data_trained_sum_bSubj_votINV$grandMean - data_trained_sum_bSubj_votINV$sd * 2.5
plus3SD = data_trained_sum_bSubj_votINV$grandMean + data_trained_sum_bSubj_votINV$sd * 3
minus3SD = data_trained_sum_bSubj_votINV$grandMean - data_trained_sum_bSubj_votINV$sd * 3

# plot
pdf("output_figures/LEALCO-EEG_votINV_outliers.pdf")
p3 <- ggplot(data_trained_sum_wSubj_votINV, aes(x=mean)) +
  geom_dotplot() +
  geom_density(alpha=.2, fill="black") +
  geom_vline(aes(xintercept=data_trained_sum_bSubj_votINV$grandMean)) +
  geom_vline(aes(xintercept=plus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus2SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus25SD), linetype="dashed") +
  geom_vline(aes(xintercept=plus3SD), linetype="dashed") +
  geom_vline(aes(xintercept=minus3SD), linetype="dashed") +
  annotate("text", x=plus2SD, y=3, label="+2SD", angle = 30) +
  annotate("text", x=minus2SD, y=3, label="-2SD", angle = 30) +
  annotate("text", x=plus25SD, y=3, label="+2.5SD", angle = 30) +
  annotate("text", x=minus25SD, y=3, label="-2.5SD", angle = 30) +
  annotate("text", x=plus3SD, y=3, label="+3SD", angle = 30) +
  annotate("text", x=minus3SD, y=3, label="-3SD", angle = 30) +
  annotate("text", x=data_trained_sum_bSubj_votINV$grandMean, y=3, label="mean", angle = 30) +
  ggtitle("Subject outliers based on naming latency (inverted)")
dev.off()
p3

# select subjects with daata beyond +/-2SDs 
data_trained_sum_wSubj_votINV[data_trained_sum_wSubj_votINV$mean < minus2SD |
                       data_trained_sum_wSubj_votINV$mean > plus2SD, ]

# select subjects with daata beyond +/-2.5SDs 
data_trained_sum_wSubj_votINV[data_trained_sum_wSubj_votINV$mean < minus25SD |
                       data_trained_sum_wSubj_votINV$mean > plus25SD, ]

# select subjects with daata beyond +/-3SDs 
data_trained_sum_wSubj_votINV[data_trained_sum_wSubj_votINV$mean < minus3SD |
                       data_trained_sum_wSubj_votINV$mean > plus3SD, ]
```

Overall, this condition-blind analysis of outliers showed that, for the **accuracy** measure, applying the following threshold results in excluding following subjects:

-   **2 SD:** 103, 144, 150

-   **2.5 SD:** -

-   **3 SD:** -

For the **(native)** **VOT** measure applying the following threshold results in excluding following subjects:

-   **2 SD:** 113, 138, 150

-   **2.5 SD:** 138, 150

-   **3 SD:** 150

For the **(inverted)** **VOT** measure applying the following threshold results in excluding following subjects:

-   **2 SD:** 121, 138, 142, 150

-   **2.5 SD:** 150

-   **3 SD:** -

In addition following subjects are excluded because they did not fulfill inclusion criteria:

-   107, 119, 129, 144

We select the exclusion criteria of +/-2.5SD on accuracy and inverted VOTs resulting in the exclusion of the following subjects.

In addition, subjects

```{r}
exclusion_acc <- c('107', '119', '129', '144')
exclusion_vot <- c('107', '119', '129', '144', '150')
exclusion_eeg <- c('101', '103', '107', '115', '119', '121', '129', '144', '150')

```

## TRIAL OVERVIEW

Here, we generate some summary statistic about trial classification (after remoing outliers).

```{r}

# select data (only on test items, but before filtering for invalid trials)
data_overview <- data %>%
  filter(class == 'test item') 
data_overview$error <- as_factor(data_overview$error)
#data_overview$error <- droplevels(data_overview$error)

# aggregte (within subject)
overview_wSubj <- data_overview %>%
  filter(!subjID %in% exclusion_acc) %>%
  group_by(subjID, error) %>%
  summarise(n = n()) %>%
  complete(error, fill = list(n = 0)) %>%
  group_by(subjID) %>%
  mutate(
    perc = n / sum(n) * 100
  ) %>%
  ungroup()

# aggregte (between subject)
overview_bSubj <- overview_wSubj %>%
  group_by(error) %>%
  summarise(count_mean = mean(n), count_sd = sd(n), perc_mean = mean(perc), perc_sd = sd(perc))

# save
write.csv(overview_bSubj, "output_stats/LEALCO-EEG_trial_overview.csv")

```

## SAMPLE STATS

Calculate LQ.

```{r}
# assign points (+/-) to the questionnaire socres
LQ <- demo[18:27]
LQ_left <- LQ
LQ_right <- LQ
LQ_left[LQ == 1] = 2
LQ_left[LQ == 2] = 1
LQ_left[LQ == 3] = 1
LQ_left[LQ == 4] = 0
LQ_left[LQ == 5] = 0
LQ_right[LQ == 1] = 0
LQ_right[LQ == 2] = 0
LQ_right[LQ == 3] = 1
LQ_right[LQ == 4] = 1
LQ_right[LQ == 5] = 2

# sum ppoints (+) for left and right
LQ_left <- LQ_left %>%
    mutate(points_left = select(., D010_02 :D010_11) %>% rowSums(na.rm = TRUE))
LQ_right <- LQ_right %>%
    mutate(points_right = select(., D010_02 :D010_11) %>% rowSums(na.rm = TRUE))
LQ$points_left <- LQ_left$points_left
LQ$points_right <- LQ_right$points_right

# calculate LQ
demo$LQ_total <- (LQ$points_right - LQ$points_left) / (LQ$points_right + LQ$points_left)
```

Generate summary stats about demographic data for our three samples.

```{r}

# full sample
sample_full <- acc_wSubj_partner <- demo %>%
  summarise(age_mean = mean(Alter), age_sd=sd(Alter),
            LQ_mean = mean(LQ_total), LQ_sd=sd(LQ_total),
            n=length(D009_01))
sample_full_sex <- demo %>%
  group_by(Gender) %>%
  summarize(n= n()) %>%
  pivot_wider(names_from=Gender, values_from=n)
sample_full <- cbind(sample_full, sample_full_sex)

# sample ACC
sample_ACC <- acc_wSubj_partner <- demo %>%
  filter(!D009_01  %in%  exclusion_acc) %>%
  summarise(age_mean = mean(Alter), age_sd=sd(Alter),
            LQ_mean = mean(LQ_total), LQ_sd=sd(LQ_total),
            n=length(D009_01))
sample_ACC_sex <- demo %>%
  filter(!D009_01  %in%  exclusion_acc) %>%
  group_by(Gender) %>%
  summarize(n= n()) %>%
  pivot_wider(names_from=Gender, values_from=n)
sample_ACC <- cbind(sample_ACC, sample_ACC_sex)

# sample VOTinv
sample_VOTinv <- acc_wSubj_partner <- demo %>%
  filter(!D009_01  %in%  exclusion_vot) %>%
  summarise(age_mean = mean(Alter), age_sd=sd(Alter),
            LQ_mean = mean(LQ_total), LQ_sd=sd(LQ_total),
            n=length(D009_01))
sample_VOTinv_sex <- demo %>%
  filter(!D009_01  %in%  exclusion_vot) %>%
  group_by(Gender) %>%
  summarize(n= n()) %>%
  pivot_wider(names_from=Gender, values_from=n)
sample_VOTinv <- cbind(sample_VOTinv, sample_VOTinv_sex)

# sample EEG
sample_EEG <- acc_wSubj_partner <- demo %>%
  filter(!D009_01  %in%  exclusion_eeg) %>%
  summarise(age_mean = mean(Alter), age_sd=sd(Alter),
            LQ_mean = mean(LQ_total), LQ_sd=sd(LQ_total),
            n=length(D009_01))
sample_EEG_sex <- demo %>%
  filter(!D009_01  %in%  exclusion_eeg) %>%
  group_by(Gender) %>%
  summarize(n= n()) %>%
  pivot_wider(names_from=Gender, values_from=n)
sample_EEG <- cbind(sample_EEG, sample_EEG_sex)

# save
write.csv(sample_full, "output_stats/LEALCO-EEG_demographic_summary_fullsample.csv")
write.csv(sample_ACC, "output_stats/LEALCO-EEG_demographic_summary_ACCsample.csv")
write.csv(sample_VOTinv, "output_stats/LEALCO-EEG_demographic_summary_VOTinvsample.csv")
write.csv(sample_EEG, "output_stats/LEALCO-EEG_demographic_summary_EEGsample.csv")
```

## ACCURACY

### By Subject (partner)

Here we just have a simple look at accuracy, that is we consider correct only those trials where the subject said *exactly* the word they were expected to say.

```{r}

# aggregte (within subject)
acc_wSubj_partner <- data_trained %>%
  filter(!subjID %in%  exclusion_acc) %>%
  group_by(subjID, partner_type) %>%
  summarise(mean = mean(correct), sd=sd(correct), sem=(sd(correct)/sqrt((length(correct)))), n=length(correct))

# save
write.csv(acc_wSubj_partner, "output_stats/LEALCO-EEG_accuracy_withinSubjects_partner.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-EEG_accuracy_withinSubjects_partner_barplot.pdf")
a <- ggplot(acc_wSubj_partner, aes(y=mean, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
    scale_fill_manual(values = pal1) +
  labs(y="Precedent maintenance (proportion)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,1) +
  facet_wrap(~subjID)
a
dev.off() 
a
```

```{r}
# aggregte (between subject)
acc_bSubj_partner <- acc_wSubj_partner %>%
  group_by(partner_type) %>%
  summarise(mean_bSubj = mean(mean), sd_bSubj=sd(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(acc_bSubj_partner, "output_stats/LEALCO-EEG_accuracy_betweenSubjects_partner.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-EEG_accuracy_betweenSubjects_partner_barplot.pdf")
c <- ggplot(acc_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  scale_fill_manual(values = pal1) +
  labs(y="Precedent maintenance (proportion)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,1)
c
dev.off()
c

# make other more transparent plot
pdf("output_figures/LEALCO-EEG_accuracy_betweenSubjects_partner_pointplot.pdf")
zz <- ggplot(acc_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_point(data= acc_wSubj_partner, aes(y=mean, x=partner_type, color=partner_type), stat="identity", position = position_jitter(w = 0.05), size=3) + 
  scale_colour_manual(values = pal1) +
    geom_point(stat="identity", color = "black", position=position_dodge(), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Precedent maintenance (proportion)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,1)
zz
dev.off()
zz
```

### By Subject (partner x block)

Now we do the same procedure, but while also accounting for block

```{r}
# aggregte (within subject)
acc_wSubj_partner_block <- data_trained %>%
  filter(!subjID %in%  exclusion_acc) %>%
  group_by(subjID, partner_type, block) %>%
  summarise(mean = mean(correct), sd=sd(correct), sem=(sd(correct)/sqrt((length(correct)))), n=length(correct))

# save
write.csv(acc_wSubj_partner_block, "output_stats/LEALCO-EEG_accuracy_withinSubjects_partner_x_block.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-EEG_accuracy_withinSubjects_partner_x_block_barplot.pdf")
a <- ggplot(acc_wSubj_partner_block, aes(y=mean, x=block, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
  labs(y="Precedent maintenance (proportion)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,1) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}
# aggregte (between subject)
acc_bSubj_partner_block <- acc_wSubj_partner_block %>%
  group_by(partner_type,block) %>%
  summarise(mean_bSubj = mean(mean), sd_bSubj=sd(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(acc_bSubj_partner_block, "output_stats/LEALCO-EEG_accuracy_betweenSubjects_partner_x_block.csv", row.names = FALSE)

# plot (within subject)
pdf("output_figures/LEALCO-EEG_accuracy_betweenSubjects_partner_x_block_barplot.pdf")
c <- ggplot(acc_bSubj_partner_block, aes(y=mean_bSubj, x=block, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Precedent maintenance (proportion)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,1)
c
dev.off()
c

# more trasparent plot
pdf("output_figures/LEALCO-EEG_accuracy_betweenSubjects_partner_x_block_pointplot.pdf")
tt <- ggplot(acc_bSubj_partner_block, aes(y=mean_bSubj, x=block, fill=partner_type)) + 
  geom_point(data= acc_wSubj_partner_block, aes(y=mean, x=block, color=partner_type), stat="identity", position = position_jitterdodge(jitter.w = 0.05, dodge.width=(.9)), size=3) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", color = "black", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Precedent maintenance (proportion)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

### By Items (partner)

```{r}

# aggregte (within item)
acc_wItem_partner <- data_trained %>%
  group_by(target_label, partner_type) %>%
    summarise(mean = mean(correct), sd=sd(correct), sem=(sd(correct)/sqrt((length(correct)))), n=length(correct))

# save
write.csv(acc_wItem_partner, "output_stats/LEALCO-EEG_accuracy_withinItems_partner.csv", row.names = FALSE)

# plot (within item)
pdf("output_figures/LEALCO-EEG_accuracy_withinItems_partner_barplot.pdf")
a <- ggplot(acc_wItem_partner, aes(y=mean, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
  labs(y="Precedent maintenance (proportion)", x="Partner") +
  theme(axis.text=element_text(size=8), axis.title=element_text(size=16)) +
  ylim(0,1) +
  facet_wrap(~target_label)
a
dev.off()
a
```

### LMM

Prepare the ACC data for LMMs.

```{r}
# for each trial, cretae new variable containing the perceived quality of teamwork, dependin gon the current partner (this just takes the correct value from the debfirefing questionnaire, depending on which partner the trial took place with)
data_trained$team  <- ifelse(data_trained$partner == 'A', data_trained$T101, data_trained$T201)

# select data
acc <- data_trained %>%
  filter(!subjID %in%  exclusion_acc)

# change the base level of the Belief and Desire condition to be B+ and D+
#TOM$conditionB <- relevel(TOM$conditionB,  'B+')  
#TOM$conditionD <- relevel(TOM$conditionD, 'D+')  

# Set sum contrasts for all variables.
acc$partner_type <- droplevels(acc$partner_type)
contrasts(acc$partner_type) <- contr.sum(2)
contrasts(acc$block)  <- contr.sum(2)

# check contrasts
contrasts(acc$partner_type)
contrasts(acc$block)

# center covariates
acc <- acc %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

acc <- acc %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

acc <- acc %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

acc <- acc %>%
  mutate(c_offset = offset - mean(offset, na.rm=TRUE))

acc <- acc %>%
  mutate(team = team - mean(team, na.rm=TRUE))
```

Try to find the maximally convergent model by using the *buildmer()* approach.

**/!\\ MIGHT TAKE \>1h TO RUN /!\\**

```{r}
# indicate the maximal effect srucutre (both fixend and rendom) that is motivated based on design & hypotheses
f <- correct ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness | subjID) +
     (partner_type*block | target_label)

# select the maximal model that still converges
m_acc <- buildmer(f,family=binomial, data=acc,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_acc)

# save winning model
sink(file = "output_stats/LEALCO-EEG_accuracy_LMM.txt")
summary(m_acc)
sink(file = NULL)

save_model_to_html(m_acc@model, 3, 'LEALCO-EEG_accuracy_LMM.html')
```

Make usual sanity checks for the winning model.

```{r}
# qqplot
pdf("output_figures/LEALCO-EEG_acc_lmm_qqplot.pdf")
qqnorm(residuals(m_acc))
dev.off()

# histogram
pdf("output_figures/LEALCO-EEG_acc_lmm_hist.pdf")
hist(residuals(m_acc))
dev.off()

# standardized residuals
pdf("output_figures/LEALCO-EEG_acc_lmm_residuals.pdf")
plot(residuals(m_acc))
dev.off()
```

#### \>Pos-hoc / maginal means (Block)

```{r}
# make post-hoc with no correction
m_acc.emm_none_block <-emmeans(m_acc@model, pairwise ~ block, adjust = "none")
m_acc.ph_none_block <- as.data.frame(m_acc.emm_none_block$contrasts)
write.csv(m_acc.ph_none_block,"output_stats/LEALCO-EEG_acc_ph_none_block.csv", row.names = FALSE)

# extract and save marginal means
m_acc.mm_block <- as.data.frame(m_acc.emm_none_block$emmeans)
m_acc.mm_block$emmean_untrans <- plogis(m_acc.mm_block$emmean)
m_acc.mm_block$asymp.LCL_untrans <- plogis(m_acc.mm_block$asymp.LCL)
m_acc.mm_block$asymp.UCL_untrans <- plogis(m_acc.mm_block$asymp.UCL)

# save them
write.csv(m_acc.mm_block,"output_stats/LEALCO-EEG_acc_lmm_marginal_block.csv", row.names = FALSE)

# visualize marginal means
pdf("output_figures/LEALCO-EEG_acc_lmm_marginal_block_pointplot.pdf")
tt <- ggplot(m_acc.mm_block, aes(y=emmean_untrans*100, x=block)) + 
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans*100, ymax=asymp.UCL_untrans*100), width=.2, position=position_dodge(.9)) +
  labs(y="Label Maintenance (%)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,100)
tt
dev.off()
tt
```

#### \>Pos-hoc / maginal means (Partner Type)

This follow up is done only for comparability with the previous LEALCO-BEH study.

```{r}
# make post-hoc with tukey correction
m_acc.emm_tukey_partner <-emmeans(m_acc@model, pairwise ~ partner_type, adjust = "Tukey")
m_acc.ph_tukey_partner <- as.data.frame(m_acc.emm_tukey_partner$contrasts)
write.csv(m_acc.ph_tukey_partner,"output_stats/LEALCO-EEG_acc_ph_tukey_partner.csv", row.names = FALSE)

# make post-hoc with no correction
m_acc.emm_none_partner <-emmeans(m_acc@model, pairwise ~ partner_type, adjust = "none")
m_acc.ph_none_partner <- as.data.frame(m_acc.emm_none_partner$contrasts)
write.csv(m_acc.ph_none_partner,"output_stats/LEALCO-EEG_acc_ph_none_partner.csv", row.names = FALSE)

# extract and save marginal means
m_acc.mm_partner <- as.data.frame(m_acc.emm_none_partner$emmeans)
m_acc.mm_partner$emmean_untrans <- plogis(m_acc.mm_partner$emmean)
m_acc.mm_partner$asymp.LCL_untrans <- plogis(m_acc.mm_partner$asymp.LCL)
m_acc.mm_partner$asymp.UCL_untrans <- plogis(m_acc.mm_partner$asymp.UCL)

# save them
write.csv(m_acc.mm_partner,"output_stats/LEALCO-EEG_acc_lmm_marginal_partner.csv", row.names = FALSE)

# visualize marginal means
tt <- ggplot(m_acc.mm_partner, aes(y=emmean_untrans*100, x=partner_type, color=partner_type)) + 
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans*100, ymax=asymp.UCL_untrans*100), width=.2, position=position_dodge(.9)) +
  labs(y="Label Maintenance (%)", x="Partner") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,100)
tt
ggsave("output_figures/LEALCO-EEG_acc_lmm_marginal_partner_pointplot.pdf", width=4
       , height=3.5)
```

#### \>Post-hoc / maginal means (Partner Type x Image Agreement x Concreteness)

This is a complex interaction involving a factor and to continuous predictors. We here plot the accuracy level predicted for:

-   concreteness: at min, Q1, Q2, Q3, max

-   image agreement: at all possible values

-   partner type: at both levels (same,different)

```{r}
pdf("output_figures/LEALCO-EEG_acc_lmm_marginal_partner_x_imageagreement_x_concreteness_pointplot.pdf")
b <- plot_model(m_acc,
                type = "pred",
                terms = c("c_FASQUEL_image_agreement [all]","partner_type" ,"c_FASQUEL_concreteness [quart]"), colors = pal1, mdrt.values = c("quart"), se=TRUE)
b
dev.off()
b

# b <- plot_model(m_acc,
#                 type = "pred",
#                 terms = c("c_FASQUEL_image_agreement [-0.6322191, 0, 1.097781] ","partner_type","c_FASQUEL_concreteness  [-0.8873572, 0,  1.252643]"), colors = pal1)
```

### LMM with offsets

```{r}
# indicate the maximal effect srucutre (both fixend and rendom) that is motivated based on design & hypotheses
f <- correct ~ partner_type * block * c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness  * c_offset +
     (partner_type * block * c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_offset * c_FASQUEL_concreteness *c_offset | subjID) +
     (partner_type*block*c_offset | target_label)

# select the maximal model that still converges
m_acc_offset <- buildmer(f,family=binomial, data=acc,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_acc_offset)

# save winning model
sink(file = "output_stats/LEALCO-EEG_accuracy_LMM_offset.txt")
summary(m_acc_offset)
sink(file = NULL)

```

## NAMING LATENCIES AT CORRECT TRIALS

### By Subject (native, partner)

Here we just have a simple look at naming latencies, while considering only trials that are correct. In a first moment, we just examine naming latencies in their native format, that is without any type of normalization for approximating normality. Note that the data is right-skewed, expected for latency data.

```{r}
# aggregte (within subject)
vot_wSubj_partner <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_vot) %>%
  group_by(subjID, partner_type) %>%
  summarise(mean = mean(VOT), sd=sd(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), n=length(VOT))

# save
write.csv(vot_wSubj_partner, "output_stats/LEALCO-EEG_vot_withinSubjects_partner.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-EEG_vot_withinSubjects_partner_barplot.pdf")
a <- ggplot(vot_wSubj_partner, aes(y=mean, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Partner") +
  theme(axis.text=element_text(size=8), axis.title=element_text(size=16)) +
  #ylim(0,1) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}

# aggregate (between subject)
vot_bSubj_partner <- vot_wSubj_partner %>%
  group_by(partner_type) %>%
  summarise(mean_bSubj = mean(mean), sd_bSubj=sd(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(vot_bSubj_partner, "output_stats/LEALCO-EEG_vot_betweenSubjects_partner.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-EEG_vot_betweenSubjects_partner_barplot.pdf")
c <- ggplot(vot_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16))
c
dev.off()
c

# plot (raincloud)
pdf("output_figures/LEALCO-EEG_vot_betweenSubjects_partner_pointplot.pdf")
tt <- ggplot(vot_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_point(data= vot_wSubj_partner, aes(y=mean, x=partner_type, color=partner_type), stat="identity", position = position_jitter(w = 0.05), size=3) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", color = "black", position=position_dodge(), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

### By Subjects (native, partner x block)

Now we do the same procedure, but while also accounting for block.

```{r}
# aggregte (within subject)
vot_wSubj_partner_block <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_vot) %>%
  group_by(subjID, partner_type, block) %>%
    summarise(mean = mean(VOT), sd=sd(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), n=length(VOT))

# save
write.csv(vot_wSubj_partner_block, "output_stats/LEALCO-EEG_vot_withinSubjects_partner_x_block.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-EEG_vot_withinSubjects_partner_x_block_barplot.pdf")
a <- ggplot(vot_wSubj_partner_block, aes(y=mean, x=block, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
      labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}

# aggregte (between subject)
vot_bSubj_partner_block <- vot_wSubj_partner_block %>%
  group_by(partner_type,block) %>%
    summarise(mean_bSubj = mean(mean), sd_bSubj=sd(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(vot_bSubj_partner_block, "output_stats/LEALCO-EEG_vot_betweenSubjects_partner_x_block.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-EEG_vot_betweenSubjects_partner_x_block_barplot.pdf")
c <- ggplot(vot_bSubj_partner_block, aes(y=mean_bSubj, x=block, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
    labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
c
dev.off()
c

# plot (pointplot)
pdf("output_figures/LEALCO-EEG_vot_betweenSubjects_partner_x_block_pointplot.pdf")
tt <- ggplot(vot_bSubj_partner_block, aes(y=mean_bSubj, x=block, fill=partner_type)) + 
  geom_point(data= vot_wSubj_partner_block, aes(y=mean, x=block, color=partner_type), stat="identity", position = position_jitterdodge(jitter.w = 0.05, dodge.width=(.9)), size=3) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", color = "black", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

### LMM

Prepare the VOT data for LMMs. Note that we will be running he model on inverted naming latency (1/naming latency). This results in the magnitude of the datapoints being inverted. The estimates of the models have to be read accordingly.

```{r}

# select data
votINV <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_vot)

# change the base level of the Belief and Desire condition to be B+ and D+
#TOM$conditionB <- relevel(TOM$conditionB,  'B+')  
#TOM$conditionD <- relevel(TOM$conditionD, 'D+')  

# Set sum contrasts for all variables.
votINV$partner_type <- droplevels(votINV$partner_type)
contrasts(votINV$partner_type) <- contr.sum(2)
contrasts(votINV$block)  <- contr.sum(2)

# check contrasts
contrasts(votINV$partner_type)
contrasts(votINV$block)

# center covariates
votINV <- votINV %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

votINV <- votINV %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

votINV <- votINV %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

votINV <- votINV %>%
  mutate(c_offset = offset - mean(offset, na.rm=TRUE))

votINV <- votINV %>%
  mutate(team = team - mean(team, na.rm=TRUE))


```

Try to find the maximally convergent model by using the *buildmer()* approach.

```{r}

# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- VOTinv ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness | subjID) +
     (partner_type*block | target_label)

# select the maximal model that still converges
m_votINV <- buildmer(f,data=votINV,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_votINV)

# save winning model
sink(file = "output_stats/LEALCO-EEG_votINV_LMM.txt")
summary(m_votINV)
sink(file = NULL)

save_model_to_html(m_votINV@model, 3, 'LEALCO-EEG_votINV_LMM.html')
```

Make model sanity checks. Everything seems ok.

```{r}
# qqplot
pdf("output_figures/LEALCO-EEG_votINV_lmm_qqplot.pdf")
qqnorm(residuals(m_votINV))
dev.off()

# histogram
pdf("output_figures/LEALCO-EEG_votINV_lmm_hist.pdf")
hist(residuals(m_votINV))
dev.off()

# standardized residuals
pdf("output_figures/LEALCO-EEG_votINV_lmm_residuals.pdf")
plot(residuals(m_votINV))
dev.off()
```

#### \>Post-hoc / marginal-means (Block)

```{r}
# make post-hoc with no correction
m_votINV.emm_none_block <-emmeans(m_votINV@model, pairwise ~ block, adjust = "none")
m_votINV.ph_none_block <- as.data.frame(m_votINV.emm_none_block$contrasts)
write.csv(m_votINV.ph_none_block,"output_stats/LEALCO-EEG_votINV_ph_none_block.csv", row.names = FALSE)

# extract and save marginal means
m_votINV.mm_block <- as.data.frame(m_votINV.emm_none_block$emmeans)
m_votINV.mm_block$emmean_untrans <- 1/m_votINV.mm_block$emmean
m_votINV.mm_block$asymp.LCL_untrans <- 1/m_votINV.mm_block$asymp.LCL
m_votINV.mm_block$asymp.UCL_untrans <- 1/m_votINV.mm_block$asymp.UCL

# save them
write.csv(m_votINV.mm_block,"output_stats/LEALCO-EEG_votINV_lmm_marginal_block.csv", row.names = FALSE)

# visualize marginal means
tt <- ggplot(m_votINV.mm_block, aes(y=emmean_untrans, x=block)) + 
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL_untrans, ymax=asymp.UCL_untrans), width=.2, position=position_dodge(.9)) +
  labs(y="Naming Latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1700)
tt
ggsave("output_figures/LEALCO-EEG_votINV_lmm_marginal_block_pointplot.pdf", width=4 , height=3.5)
```

#### \>Post-hoc / marginal-means (Partner Type)

```{r}
# make post-hoc with no correction (partner)
m_votINV.emm_none_partner <-emmeans(m_votINV@model, pairwise ~ partner_type, adjust = "none")
m_votINV.ph_none_partner <- as.data.frame(m_votINV.emm_none_partner$contrasts)
write.csv(m_votINV.ph_none_partner,"output_stats/LEALCO-EEG_votINV_ph_none_partner.csv", row.names = FALSE)

# extract and save marginal means (partner)
m_votINV.mm_partner <- as.data.frame(m_votINV.emm_none_partner$emmeans)
m_votINV.mm_partner$emmean_untrans <- 1/m_votINV.mm_partner$emmean
m_votINV.mm_partner$lower.CL_untrans <- 1/m_votINV.mm_partner$asymp.UCL
m_votINV.mm_partner$upper.CL_untrans <- 1/m_votINV.mm_partner$asymp.LCL
write.csv(m_votINV.mm_partner,"output_stats/LEALCO-EEG_votINV_lmm_marginal_partner.csv", row.names = FALSE)

tt <- ggplot(m_votINV.mm_partner, aes(y=emmean_untrans, x=partner_type, color=partner_type)) + 
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Partner Type") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1700)
tt
ggsave("output_figures/LEALCO-EEG_votINV_lmm_marginal_partner_pointplot.pdf", width=4 , height=3.5)
```

#### \>Post-hoc / marginal-means (Partner Type x Block)

```{r}

# make post-hoc with tukey correction
m_votINV.emm_tukey_partner_x_block <-emmeans(m_votINV@model, pairwise ~ partner_type * block, adjust = "tukey")
m_votINV.ph_tukey_partner_x_block <- as.data.frame(m_votINV.emm_tukey_partner_x_block$contrasts)
write.csv(m_votINV.ph_tukey_partner_x_block,"output_stats/LEALCO-EEG_votINV_ph_tukey_partner_x_block.csv", row.names = FALSE)

# make post-hoc with no correction
m_votINV.emm_none_partner_x_block <-emmeans(m_votINV@model, pairwise ~ partner_type * block, adjust = "none")
m_votINV.ph_none_partner_x_block <- as.data.frame(m_votINV.emm_none_partner_x_block$contrasts)
m_votINV.ph_none_partner_x_block$p.valueBonf2 = m_votINV.ph_none_partner_x_block$p.value *2
write.csv(m_votINV.ph_none_partner_x_block,"output_stats/LEALCO-EEG_votINV_ph_none_partner_x_block.csv", row.names = FALSE)

# extract and save marginal means
m_votINV.mm_partner_x_block <- as.data.frame(m_votINV.emm_tukey_partner_x_block$emmeans)
m_votINV.mm_partner_x_block$emmean_untrans <- 1/m_votINV.mm_partner_x_block$emmean
m_votINV.mm_partner_x_block$lower.CL_untrans <- 1/m_votINV.mm_partner_x_block$asymp.UCL
m_votINV.mm_partner_x_block$upper.CL_untrans <- 1/m_votINV.mm_partner_x_block$asymp.LCL
write.csv(m_votINV.mm_partner_x_block,"output_stats/LEALCO-EEG_votINV_lmm_marginal_partner_x_block.csv", row.names = FALSE)

# plot
tt <- ggplot(m_votINV.mm_partner_x_block, aes(y=emmean_untrans, x=block, color=partner_type)) + 
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
  labs(y="Naming Latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1700)
tt
ggsave("output_figures/LEALCO-EEG_votINV_lmm_marginal_partner_x_block_pointplot.pdf", width=4 , height=3.5)
```

For exploratory reasons, we also tested the same maximal model while adding the interaction with *team* in the fixed structure. Some complex interactions wit the variable *team* come out. Yet, because they are 3- and 4-way interactions, they are complicated to interpret.

### LMM with offset

```{r}

# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- VOTinv ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * c_offset +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * c_offset | subjID) +
     (partner_type*block * c_offset | target_label)

# select the maximal model that still converges
m_votINV_offset <- buildmer(f,data=votINV,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_votINV_offset)

# save winning model
sink(file = "output_stats/LEALCO-EEG_votINV_LMM_offset.txt")
summary(m_votINV_offset)
sink(file = NULL)
```

## P200 AT CORRECT RIALS

### By Subject (native, partner)

Here we just have a simple look at P200, while considering only trials that are correct.

```{r}
# aggregte (within subject)
P200_wSubj_partner <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_eeg) %>%
  group_by(subjID, partner_type) %>%
  summarise(mean = mean(P200, na.rm=TRUE), sd=sd(P200, na.rm=TRUE), sem=(sd(P200, na.rm=TRUE)/sqrt((length(P200)))), n=length(P200))

# save
write.csv(P200_wSubj_partner, "output_stats/LEALCO-EEG_P200_withinSubjects_partner.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-EEG_p200_withinSubjects_partner_barplot.pdf")
a <- ggplot(P200_wSubj_partner, aes(y=mean, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2, position=position_dodge(.9)) +
  labs(y="P200 (\u00b5V)", x="Partner") +
  theme(axis.text=element_text(size=8), axis.title=element_text(size=16)) +
  #ylim(0,1) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}

# aggregate (between subject)
P200_bSubj_partner <- P200_wSubj_partner %>%
  group_by(partner_type) %>%
  summarise(mean_bSubj = mean(mean ,na.rm=TRUE), sd_bSubj=sd(mean ,na.rm=TRUE), sem_bSubj=(sd(mean, na.rm=TRUE)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(P200_bSubj_partner, "output_stats/LEALCO-EEG_p200_betweenSubjects_partner.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-EEG_p200_betweenSubjects_partner_barplot.pdf")
c <- ggplot(P200_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="P200 (\u00b5V)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16))
c
dev.off()
c

# plot (raincloud)
pdf("output_figures/LEALCO-EEG_P200_betweenSubjects_partner_pointplot.pdf")
tt <- ggplot(P200_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_point(data= P200_wSubj_partner, aes(y=mean, x=partner_type, color=partner_type), stat="identity", position = position_jitter(w = 0.05), size=3) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", color = "black", position=position_dodge(), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="P200 (\u00b5V)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt

```

### By Subjects (native, partner x block)

Now we do the same procedure, but while also accounting for block.

```{r}
# aggregte (within subject)
P200_wSubj_partner_block <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_eeg) %>%
  group_by(subjID, partner_type, block) %>%
    summarise(mean = mean(P200, na.rm=TRUE), sd=sd(P200, na.rm=TRUE), sem=(sd(P200, na.rm=TRUE)/sqrt((length(P200)))), n=length(P200))

# save
write.csv(P200_wSubj_partner_block, "output_stats/LEALCO-EEG_P200_withinSubjects_partner_x_block.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-EEG_P200_withinSubjects_partner_x_block_barplot.pdf")
a <- ggplot(P200_wSubj_partner_block, aes(y=mean, x=block, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
      labs(y="P200 (\u00b5V)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}
# aggregte (between subject)
P200_bSubj_partner_block <- P200_wSubj_partner_block %>%
  group_by(partner_type,block) %>%
    summarise(mean_bSubj = mean(mean, na.rm=TRUE), sd_bSubj=sd(mean, na.rm=TRUE), sem_bSubj=(sd(mean, na.rm=TRUE)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(P200_bSubj_partner_block, "output_stats/LEALCO-EEG_P200_betweenSubjects_partner_x_block.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-EEG_P200_betweenSubjects_partner_x_block_barplot.pdf")
c <- ggplot(P200_bSubj_partner_block, aes(y=mean_bSubj, x=block, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
    labs(y="P200 (\u00b5V)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
c
dev.off()
c

# plot (pointplot)
pdf("output_figures/LEALCO-EEG_P200_betweenSubjects_partner_x_block_pointplot.pdf")
tt <- ggplot(P200_bSubj_partner_block, aes(y=mean_bSubj, x=block, fill=partner_type)) + 
  geom_point(data= P200_wSubj_partner_block, aes(y=mean, x=block, color=partner_type), stat="identity", position = position_jitterdodge(jitter.w = 0.05, dodge.width=(.9)), size=3) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", color = "black", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="P200 (\u00b5V)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

### LMM

Prepare the P200data for LMMs.

```{r}

# select data
P200 <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_eeg)

# change the base level of the Belief and Desire condition to be B+ and D+
#TOM$conditionB <- relevel(TOM$conditionB,  'B+')  
#TOM$conditionD <- relevel(TOM$conditionD, 'D+')  

# Set sum contrasts for all variables.
P200$partner_type <- droplevels(P200$partner_type)
contrasts(P200$partner_type) <- contr.sum(2)
contrasts(P200$block)  <- contr.sum(2)

# check contrasts
contrasts(P200$partner_type)
contrasts(P200$block)

# center covariates
P200 <- P200 %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

P200 <- P200 %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

P200 <- P200 %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

P200 <- P200 %>%
  mutate(c_offset = offset - mean(offset, na.rm=TRUE))

P200 <- P200 %>%
  mutate(team = team - mean(team, na.rm=TRUE))
```

Try to find the maximally convergent model by using the *buildmer()* approach.

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P200 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness | subjID) +
     (partner_type*block | target_label)

# select the maximal model that still converges
m_P200 <- buildmer(f,data=P200,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P200)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P200_LMM.txt")
summary(m_P200)
sink(file = NULL)

save_model_to_html(m_P200@model, 3, 'LEALCO-EEG_P200_LMM.html')
```

Sanity check

```{r}
# qqplot
pdf("output_figures/LEALCO-EEG_P200_lmm_qqplot.pdf")
qqnorm(residuals(m_P200))
dev.off()

# histogram
pdf("output_figures/LEALCO-EEG_P200_lmm_hist.pdf")
hist(residuals(m_P200))
dev.off()

# standardized residuals
pdf("output_figures/LEALCO-EEG_P200_lmm_residuals.pdf")
plot(residuals(m_P200))
dev.off()
```

#### \>Follow-up: Partner x Block (which is n.s.!)

Note that this specific interaction is not significant. However, let's still have a look as a sanity check, to make sure that visually, the effect has the directionality we expect. Calculate emmeans and post-hocs for partner x block.

```{r}
# make post-hoc with tukey correction (partner x block)
emm_tukey <-emmeans(m_P200@model, pairwise ~ partner_type * block, adjust = "Tukey")
P200_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P200_ph_tukey,"output_stats/LEALCO-EEG_P200_ph_tukey_partner_x_block.csv", row.names = FALSE)

# make post-hoc with no correction (partner x block)
emm_none <-emmeans(m_P200@model, pairwise ~ partner_type * block, adjust = "none")
P200_ph_none <- as.data.frame(emm_none$contrasts)
write.csv(P200_ph_none,"output_stats/LEALCO-EEG_P200_ph_none_partner_x_block.csv", row.names = FALSE)

# extract and save marginal means (partner x block)
P200_marginalMeans <- as.data.frame(emm_tukey$emmeans)
write.csv(P200_marginalMeans,"output_stats/LEALCO-EEG_P200_lmm_marginal_partner_x_block.csv", row.names = FALSE)

tt <- ggplot(P200_marginalMeans, aes(y=emmean, x=block, color=partner_type)) + 
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), width=.2, position=position_dodge(.9)) +
  labs(y="P200 (\u00b5V)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  geom_hline(yintercept=0, linetype=3) +
  ylim(-4,14)
tt
ggsave("output_figures/LEALCO-EEG_P200_lmm_marginal_partner_x_block_pointplot.pdf", width = 4, height = 3)
```

#### \>Follow-up: Partner x Block x Concreteness

```{r}


# make post-hoc with no correction
emm_none <-emmeans(m_P200@model, pairwise ~ partner_type * block * c_FASQUEL_concreteness, adjust = "none")
P200_ph_none <- as.data.frame(emm_none$contrasts)
write.csv(P200_ph_none,"output_stats/LEALCO-EEG_P200_ph_none_partner_x_block_x_concretness.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P200@model, pairwise ~ partner_type * block * c_FASQUEL_concreteness, adjust = "none", , cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P200_ph_none <- as.data.frame(emm_none$contrasts)
P200_ph_none$Bonf2 <- P200_ph_none$p.value * 2
P200_ph_none$Bonf3 <- P200_ph_none$p.value * 3
write.csv(P200_ph_none,"output_stats/LEALCO-EEG_P200_ph_none_partner_x_block_x_concretness.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(c_FASQUEL_concreteness=c(min(P200$c_FASQUEL_concreteness),max(P200$c_FASQUEL_concreteness)),
                partner_type=c("same","different"),
                block=c('1', '2')))
P200_marginalMeans <- emmip(m_P200@model, c_FASQUEL_concreteness  ~ block ~ partner_type, at=mylist,CIs=TRUE, plotit=FALSE)

#P200_marginalMeans <- as.data.frame(emm_tukey$emmeans)
write.csv(P200_marginalMeans,"output_stats/LEALCO-EEG_P200_lmm_marginal_partner_x_block_x_concretness.csv", row.names = FALSE)

# plot
pdf("output_figures/LEALCO-EEG_P200_lmm_marginal_partner_x_block_x_concretness.pdf")
b <- ggplot(P200_marginalMeans, aes(x=c_FASQUEL_concreteness, y=yvar, color=partner_type, group=partner_type))+
  geom_line() + 
  geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  facet_grid(~ block) + 
  labs(y="P200 (\u00b5V)", x="Concreteness") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) 
dev.off()
b
```

#### \>Follow-up: Partner x Block x Concreteness x Image Agreement

```{r}

# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P200@model, pairwise ~ partner_type * block * c_FASQUEL_concreteness * c_FASQUEL_image_agreement, adjust = "Tukey")
P200_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P200_ph_tukey,"output_stats/LEALCO-EEG_P200_ph_tukey_partner_x_block_x_concretness_x_agreement.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P200@model, pairwise ~ partner_type * block * c_FASQUEL_concreteness * c_FASQUEL_image_agreement, adjust = "none")
P200_ph_none <- as.data.frame(emm_none$contrasts)
write.csv(P200_ph_none,"output_stats/LEALCO-EEG_P200_ph_none_partner_x_block_x_concretness_x_agreement.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(c_FASQUEL_concreteness=c(min(P200$c_FASQUEL_concreteness),max(P200$c_FASQUEL_concreteness)),
                c_FASQUEL_image_agreement=c(min(P200$c_FASQUEL_image_agreement),max(P200$c_FASQUEL_image_agreement)),
                partner_type=c("same","different"),
                block=c('1', '2')))
P200_marginalMeans <- emmip(m_P200@model, c_FASQUEL_concreteness ~ c_FASQUEL_image_agreement ~ block ~ partner_type, at=mylist,CIs=TRUE, plotit=FALSE)

#P200_marginalMeans <- as.data.frame(emm_tukey$emmeans)
write.csv(P200_marginalMeans,"output_stats/LEALCO-EEG_P200_lmm_marginal_partner_x_block_x_concretness_x_agreement.csv", row.names = FALSE)

# plot
pdf("output_figures/LEALCO-EEG_P200_lmm_marginal_partner_x_block_x_concretness_x_agreement.pdf")
bb <- ggplot(P200_marginalMeans, aes(x=block, y=yvar, color=partner_type, group=partner_type))+
  geom_line() + 
  geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  facet_grid(c_FASQUEL_concreteness ~ c_FASQUEL_image_agreement) + 
  labs(y="P200 (\u00b5V)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) 
dev.off()
bb
```

### LLM (\~acc)

```{r}

```

### LMM (only block 1)

```{r}
# P200 <- P200 %>%
#   filter(block == 1)
```

```{r}
# # indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
# f <- P200 ~ partner_type*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
#      (partner_type*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
#      (partner_type | target_label)
# 
# # select the maximal model that still converges
# m_P200 <- buildmer(f,data=P200,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
# summary(m_P200)
# 
# # save winning model
# sink(file = "output_stats/LEALCO-EEG_P200b1_LMM.txt")
# summary(m_P200)
# sink(file = NULL)
```

### LMM with offset

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P200 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * c_offset +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * c_offset| subjID) +
     (partner_type*block * c_offset| target_label)

# select the maximal model that still converges
m_P200_offset <- buildmer(f,data=P200,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P200_offset)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P200_LMM_offset.txt")
summary(m_P200_offset)
sink(file = NULL)
```

## P200 AT ALL TRIALS

### LMM accounting for behavior

```{r}
# select data
P200_all <- data_trained %>%
  filter(!subjID %in%  exclusion_eeg)

# make accuracy a factor
P200_all$f_correct <- as.factor(P200_all$correct)

# change the base level of the Belief and Desire condition to be B+ and D+
P200_all$correct <- relevel(P200_all$f_correct,  '1')

# Set sum contrasts for all variables.
P200_all$partner_type <- droplevels(P200_all$partner_type)
contrasts(P200_all$partner_type) <- contr.sum(2)
contrasts(P200_all$block)  <- contr.sum(2)
contrasts(P200_all$f_correct)  <- contr.sum(2)

# check contrasts
contrasts(P200_all$partner_type)
contrasts(P200_all$block)
contrasts(P200_all$f_correct)

# center covariates
P200_all <- P200_all %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

P200_all <- P200_all %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

P200_all <- P200_all %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

P200_all <- P200_all %>%
  mutate(team = team - mean(team, na.rm=TRUE))
```

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P200 ~ correct*partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (correct*partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness | subjID) +
     (correct*partner_type*block | target_label)

# select the maximal model that still converges
m_P200acc <- buildmer(f,data=P200_all,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P200acc)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P200acc_LMM.txt")
summary(m_P200acc)
sink(file = NULL)
```

#### \>Follow-up: Partner x Block x Concreteness

```{r}

# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P200acc@model, pairwise ~ partner_type * block * c_FASQUEL_concreteness, adjust = "Tukey")
P200_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P200_ph_tukey,"output_stats/LEALCO-EEG_P200acc_ph_tukey_partner_x_block_x_concretness.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P200acc@model, pairwise ~ partner_type * block * c_FASQUEL_concreteness, adjust = "none")
P200_ph_none <- as.data.frame(emm_none$contrasts)
write.csv(P200_ph_none,"output_stats/LEALCO-EEG_P200acc_ph_none_partner_x_block_x_concretness.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(c_FASQUEL_concreteness=c(min(P200_all$c_FASQUEL_concreteness),max(P200_all$c_FASQUEL_concreteness)),
                partner_type=c("same","different"),
                block=c('1', '2')))
P200_marginalMeans <- emmip(m_P200acc@model, c_FASQUEL_concreteness ~ block ~ partner_type, at=mylist,CIs=TRUE, plotit=FALSE)

#P200_marginalMeans <- as.data.frame(emm_tukey$emmeans)
write.csv(P200_marginalMeans,"output_stats/LEALCO-EEG_P200acc_lmm_marginal_partner_x_block_x_concretness.csv", row.names = FALSE)

# plot
pdf("output_figures/LEALCO-EEG_P200acc_lmm_marginal_partner_x_block_x_concretness.pdf")
ggplot(P200_marginalMeans, aes(x=c_FASQUEL_concreteness, y=yvar, color=partner_type, group=partner_type))+
  geom_line() +
  geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  facet_grid(~block) +
  labs(y="P200 (\u00b5V)", x="Concreteness (centered)") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16))
dev.off()
```

## P300 AT CORRECT RIALS

### By Subject (native, partner)

Here we just have a simple look at P300, while considering only trials that are correct.

```{r}
# aggregte (within subject)
P300_wSubj_partner <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_eeg) %>%
  group_by(subjID, partner_type) %>%
  summarise(mean = mean(P300, na.rm=TRUE), sd=sd(P300, na.rm=TRUE), sem=(sd(P300, na.rm=TRUE)/sqrt((length(P300)))), n=length(P300))

# save
write.csv(P300_wSubj_partner, "output_stats/LEALCO-EEG_P300_withinSubjects_partner.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-EEG_P300_withinSubjects_partner_barplot.pdf")
a <- ggplot(P300_wSubj_partner, aes(y=mean, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2, position=position_dodge(.9)) +
  labs(y="P300 (\u00b5V)", x="Partner") +
  theme(axis.text=element_text(size=8), axis.title=element_text(size=16)) +
  #ylim(0,1) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}

# aggregate (between subject)
P300_bSubj_partner <- P300_wSubj_partner %>%
  group_by(partner_type) %>%
  summarise(mean_bSubj = mean(mean ,na.rm=TRUE), sd_bSubj=sd(mean ,na.rm=TRUE), sem_bSubj=(sd(mean, na.rm=TRUE)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(P300_bSubj_partner, "output_stats/LEALCO-EEG_P300_betweenSubjects_partner.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-EEG_P300_betweenSubjects_partner_barplot.pdf")
c <- ggplot(P300_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="P300 (\u00b5V)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16))
c
dev.off()
c

# plot (raincloud)
pdf("output_figures/LEALCO-EEG_P300_betweenSubjects_partner_pointplot.pdf")
tt <- ggplot(P300_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_point(data= P300_wSubj_partner, aes(y=mean, x=partner_type, color=partner_type), stat="identity", position = position_jitter(w = 0.05), size=3) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", color = "black", position=position_dodge(), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="P300 (\u00b5V)", x="Partner") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt

```

### By Subjects (native, partner x block)

Now we do the same procedure, but while also accounting for block.

```{r}
# aggregte (within subject)
P300_wSubj_partner_block <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_eeg) %>%
  group_by(subjID, partner_type, block) %>%
    summarise(mean = mean(P300, na.rm=TRUE), sd=sd(P300, na.rm=TRUE), sem=(sd(P300, na.rm=TRUE)/sqrt((length(P300)))), n=length(P300))

# save
write.csv(P300_wSubj_partner_block, "output_stats/LEALCO-EEG_P300_withinSubjects_partner_x_block.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-EEG_P300_withinSubjects_partner_x_block_barplot.pdf")
a <- ggplot(P300_wSubj_partner_block, aes(y=mean, x=block, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
      labs(y="P300 (\u00b5V)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}
# aggregte (between subject)
P300_bSubj_partner_block <- P300_wSubj_partner_block %>%
  group_by(partner_type,block) %>%
    summarise(mean_bSubj = mean(mean, na.rm=TRUE), sd_bSubj=sd(mean, na.rm=TRUE), sem_bSubj=(sd(mean, na.rm=TRUE)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(P300_bSubj_partner_block, "output_stats/LEALCO-EEG_P300_betweenSubjects_partner_x_block.csv", row.names = FALSE)

# plot (barplot)
pdf("output_figures/LEALCO-EEG_P300_betweenSubjects_partner_x_block_barplot.pdf")
c <- ggplot(P300_bSubj_partner_block, aes(y=mean_bSubj, x=block, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal1) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
    labs(y="P300 (\u00b5V)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
c
dev.off()
c

# plot (pointplot)
pdf("output_figures/LEALCO-EEG_P300_betweenSubjects_partner_x_block_pointplot.pdf")
tt <- ggplot(P300_bSubj_partner_block, aes(y=mean_bSubj, x=block, fill=partner_type)) + 
  geom_point(data= P300_wSubj_partner_block, aes(y=mean, x=block, color=partner_type), stat="identity", position = position_jitterdodge(jitter.w = 0.05, dodge.width=(.9)), size=3) +
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", color = "black", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="P300 (\u00b5V)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

### LMM

Prepare the P300data for LMMs.

```{r}
# select data
P300 <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_eeg)

# change the base level of the Belief and Desire condition to be B+ and D+
#TOM$conditionB <- relevel(TOM$conditionB,  'B+')  
#TOM$conditionD <- relevel(TOM$conditionD, 'D+')  

# Set sum contrasts for all variables.
P300$partner_type <- droplevels(P300$partner_type)
contrasts(P300$partner_type) <- contr.sum(2)
contrasts(P300$block)  <- contr.sum(2)

# check contrasts
contrasts(P300$partner_type)
contrasts(P300$block)

# center covariates
P300 <- P300 %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

P300 <- P300 %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

P300 <- P300 %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

P300 <- P300 %>%
  mutate(c_offset = offset - mean(offset, na.rm=TRUE))

P300 <- P300 %>%
  mutate(team = team - mean(team, na.rm=TRUE))
```

Run the model

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P300 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness | subjID) +
     (partner_type*block | target_label)

# select the maximal model that still converges
m_P300 <- buildmer(f,data=P300,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P300)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P300_LMM.txt")
summary(m_P300)
sink(file = NULL)

save_model_to_html(m_P300@model, 3, 'LEALCO-EEG_P300_LMM.html')
```

Model diagnostics

```{r}
# qqplot
pdf("output_figures/LEALCO-EEG_P300_lmm_qqplot.pdf")
qqnorm(residuals(m_P300))
dev.off()

# histogram
pdf("output_figures/LEALCO-EEG_P300_lmm_hist.pdf")
hist(residuals(m_P300))
dev.off()

# standardized residuals
pdf("output_figures/LEALCO-EEG_P300_lmm_residuals.pdf")
plot(residuals(m_P300))
dev.off()
```

### \>Follow up: Partner x Block (which is n.s.!)

```{r}
# make post-hoc with tukey correction (partner x block)
emm_tukey <-emmeans(m_P300@model, pairwise ~ partner_type * block, adjust = "Tukey")
P300_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P300_ph_tukey,"output_stats/LEALCO-EEG_P300_ph_tukey_partner_x_block.csv", row.names = FALSE)

# make post-hoc with no correction (partner x block)
emm_none <-emmeans(m_P300@model, pairwise ~ partner_type * block, adjust = "none")
P300_ph_none <- as.data.frame(emm_none$contrasts)
write.csv(P300_ph_none,"output_stats/LEALCO-EEG_P300_ph_none_partner_x_block.csv", row.names = FALSE)
```

```{r}
# extract and save marginal means (partner x block)
P300_marginalMeans <- as.data.frame(emm_tukey$emmeans)
write.csv(P300_marginalMeans,"output_stats/LEALCO-EEG_P300_lmm_marginal_partner_x_block.csv", row.names = FALSE)

tt <- ggplot(P300_marginalMeans, aes(y=emmean, x=block, color=partner_type)) + 
  scale_colour_manual(values = pal1) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), width=.2, position=position_dodge(.9)) +
  labs(y="P300 (\u00b5V)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  geom_hline(yintercept=0, linetype=3) +
  ylim(-4,14)
tt
ggsave("output_figures/LEALCO-EEG_P300_lmm_marginal_partner_x_block_pointplot.pdf", width = 4, height = 3)
```

### \>Follow up: Image Agreement x Partner Type x Block x Concreteness x Frequency

```{r}

# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P300@model, pairwise ~ partner_type * block * c_FASQUEL_concreteness * c_FASQUEL_image_agreement * c_SUBTLEX_frequency_log, adjust = "Tukey")
P300_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P300_ph_tukey,"output_stats/LEALCO-EEG_P300_ph_tukey_partner_x_block_x_concretness_x_agreement_x_frequency.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P300@model, pairwise ~ partner_type * block * c_FASQUEL_concreteness * c_FASQUEL_image_agreement, adjust = "none")
P300_ph_none <- as.data.frame(emm_none$contrasts)
write.csv(P300_ph_none,"output_stats/LEALCO-EEG_P300_ph_none_partner_x_block_x_concretness_x_agreement_x_frequency.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(c_FASQUEL_concreteness=c(min(P300$c_FASQUEL_concreteness),max(P300$c_FASQUEL_concreteness)),
                c_FASQUEL_image_agreement=c(min(P300$c_FASQUEL_image_agreement),max(P300$c_FASQUEL_image_agreement)),
                c_SUBTLEX_frequency_log=c(min(P300$c_SUBTLEX_frequency_log),max(P300$c_SUBTLEX_frequency_log)),
                partner_type=c("same","different"),
                block=c('1', '2')))
P300_marginalMeans <- emmip(m_P300@model, c_FASQUEL_concreteness ~ c_FASQUEL_image_agreement ~ block ~ partner_type ~ c_SUBTLEX_frequency_log, at=mylist,CIs=TRUE, plotit=FALSE)

#P300_marginalMeans <- as.data.frame(emm_tukey$emmeans)
write.csv(P300_marginalMeans,"output_stats/LEALCO-EEG_P300_lmm_marginal_partner_x_block_x_concretness_x_agreement_x_frequency.csv", row.names = FALSE)

# plot
pdf("output_figures/LEALCO-EEG_P300_lmm_marginal_partner_x_block_x_concretness_x_agreement_x_frequency.pdf")
ggplot(P300_marginalMeans, aes(x=block, y=yvar, color=partner_type, group=partner_type))+
  geom_line() + 
  geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  facet_grid(c_FASQUEL_concreteness ~ c_FASQUEL_image_agreement ~ c_SUBTLEX_frequency_log) + 
  labs(y="P300 (\u00b5V)", x="Block") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) 
dev.off()
```

### LMM (only block 1)

```{r}
# P300 <- P300 %>%
#   filter(block == 1)
```

```{r}
# # indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
# f <- P300 ~ partner_type*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
#      (partner_type*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
#      (partner_type | target_label)
# 
# # select the maximal model that still converges
# m_P300 <- buildmer(f,data=P300,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
# summary(m_P300)
# 
# # save winning model
# sink(file = "output_stats/LEALCO-EEG_P300b1_LMM.txt")
# summary(m_P300)
# sink(file = NULL)
```

### LMM accounting for VOTinv

```{r}
# # select data
# P300votinv <- data_trained %>%
#   filter(!subjID %in%  exclusion_eeg) %>%
#   filter(correct == 1)
# 
# # indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
# f <- P300 ~ VOTinv*partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
#      (correct*partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
#      (correct*partner_type*block | target_label)
#   
# # select the maximal model that still converges
# m_P300 <- buildmer(f,data=P300,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
# summary(m_P300)
# 
# # save winning model
# sink(file = "output_stats/LEALCO-EEG_P300votinv_LMM.txt")
# summary(m_P300)
# sink(file = NULL)
```

### LMM with offset

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P300 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * c_offset +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness* c_offset | subjID) +
     (partner_type*block* c_offset | target_label)

# select the maximal model that still converges
m_P300_offset <- buildmer(f,data=P300,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P300_offset)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P300_LMM_offset.txt")
summary(m_P300_offset)
sink(file = NULL)
```

## P300 AT ALL TRIALS

### LMM accounting for behavior

```{r}

# select data
P300_all <- data_trained %>%
  filter(!subjID %in%  exclusion_eeg)

# make accuracy a factor
P300_all$f_correct <- as.factor(P300_all$correct)

# change the base level of the Belief and Desire condition to be B+ and D+
P300_all$correct <- relevel(P300_all$f_correct,  '1')

# Set sum contrasts for all variables.
P300_all$partner_type <- droplevels(P300_all$partner_type)
contrasts(P300_all$partner_type) <- contr.sum(2)
contrasts(P300_all$block)  <- contr.sum(2)
contrasts(P300_all$f_correct)  <- contr.sum(2)

# check contrasts
contrasts(P300_all$partner_type)
contrasts(P300_all$block)
contrasts(P300_all$f_correct)

# center covariates
P300_all <- P300_all %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

P300_all <- P300_all %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

P300_all <- P300_all %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

P300_all <- P300_all %>%
  mutate(team = team - mean(team, na.rm=TRUE))

# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P300 ~ correct*partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (correct*partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
     (correct*partner_type*block | target_label)

# select the maximal model that still converges
m_P300acc <- buildmer(f,data=P300_all,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P300acc)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P300acc_LMM.txt")
summary(m_P300acc)
sink(file = NULL)
```

```{r}
# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P300acc@model, pairwise ~ partner_type * block * c_FASQUEL_concreteness, adjust = "Tukey")
P300_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P300_ph_tukey,"output_stats/LEALCO-EEG_P300acc_ph_tukey_partner_x_block_x_concretness.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P300acc@model, pairwise ~ partner_type * block * c_FASQUEL_concreteness, adjust = "none")
P300_ph_none <- as.data.frame(emm_none$contrasts)
write.csv(P300_ph_none,"output_stats/LEALCO-EEG_P300acc_ph_none_partner_x_block_x_concretness.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(c_FASQUEL_concreteness=c(min(P300_all$c_FASQUEL_concreteness),max(P300_all$c_FASQUEL_concreteness)),
                partner_type=c("same","different"),
                block=c('1', '2')))
P300_marginalMeans <- emmip(m_P300acc@model, c_FASQUEL_concreteness ~ block ~ partner_type, at=mylist,CIs=TRUE, plotit=FALSE)

#P300_marginalMeans <- as.data.frame(emm_tukey$emmeans)
write.csv(P300_marginalMeans,"output_stats/LEALCO-EEG_P300acc_lmm_marginal_partner_x_block_x_concretness.csv", row.names = FALSE)

# plot
pdf("output_figures/LEALCO-EEG_P300acc_lmm_marginal_partner_x_block_x_concretness.pdf")
ggplot(P300_marginalMeans, aes(x=c_FASQUEL_concreteness, y=yvar, color=partner_type, group=partner_type))+
  geom_line() +
  geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  facet_grid(~block) +
  labs(y="P300 (\u00b5V)", x="Concreteness (centered)") +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16))
dev.off()
```

## ENTRAINMENT

```{r}
# aggregte accuracy (within subject)
acc_wSubj_partner <- data_trained %>%
  filter(!subjID %in%  exclusion_acc) %>%
  group_by(subjID, partner_type) %>%
  summarise(mean_ACC = mean(correct))

# aggregate VOTinv (within subjects) only for correct trials
vot_wSubj_partner <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_vot) %>%
  group_by(subjID, partner_type) %>%
  summarise(mean_VOT = mean(VOT))

# aggregate VOTinv (within subjects) only for correct trials
votINV_wSubj_partner <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_vot) %>%
  group_by(subjID, partner_type) %>%
  summarise(mean_VOTinv = mean(VOTinv))

# aggregate EEG data (within subjects) only for correct trials
EEG_wSubj_partner <- data_trained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_eeg) %>%
  group_by(subjID, partner_type) %>%
  summarise(mean_P200 = mean(P200, na.rm=TRUE), mean_P300 = mean(P300, na.rm=TRUE) )

# merge all aggragated DVs
entrainment_data <- merge(acc_wSubj_partner, vot_wSubj_partner,by=c("subjID","partner_type"))
entrainment_data <- merge(x = entrainment_data, y = votINV_wSubj_partner, by = c("subjID", "partner_type"), all.x = TRUE)
entrainment_data <- merge(x = entrainment_data, y = EEG_wSubj_partner, by = c("subjID", "partner_type"), all.x = TRUE)

# pivot from long to wide
entrainment_data <- entrainment_data %>% 
  pivot_wider(
    names_from = partner_type, 
    values_from = c(mean_ACC, mean_VOT, mean_VOTinv, mean_P200, mean_P300)
  )

```

#### Version 1 (with inverted VOT)

```{r}

 # calculate entrainment scores (same - different)
entrainment_data$entrainment_ACC <- entrainment_data$mean_ACC_same - entrainment_data$mean_ACC_different
entrainment_data$entrainment_VOTinv <- (entrainment_data$mean_VOTinv_same - entrainment_data$mean_VOTinv_different) * 10000

# correlation
corr <- cor.test(entrainment_data$entrainment_ACC, entrainment_data$entrainment_VOTinv)
sink('output_stats/LEALCO-EEG_entrainment_correlation_invVOT.txt')
print(corr)
sink()

# format for plot
if (corr$p.value < 0.001) {
  txt <- paste0('R=', round(corr$estimate, digits = 3), "\np<0.001")
} else {
  txt <- paste0('R=', round(corr$estimate, digits = 3), "\np=", round(corr$p.value, digits = 3) )
}

# scatterplot
s <- ggplot(entrainment_data, aes(x=entrainment_VOTinv, y=entrainment_ACC)) +
  geom_point() +
  stat_smooth(method=lm, fullrange=TRUE, color = 'black') + 
  geom_hline(yintercept=0, linetype="dotted") +
  geom_vline(xintercept=0, linetype="dotted") +
  xlim(-2.5, 2.5) +
  ylim(-0.5, 0.5) + 
  geom_text(x=1.5, y=-0.4, label=txt) +
  xlab('Partner-Specific Naming Latency\n(same vs. different)') +
  ylab('Partner-Specific Label Maintenance\n(same vs. different)') +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=12)) 
s
ggsave("output_figures/LEALCO-EEG_entrainment_correlation_invVOT.pdf", width=6, height=3.5)


```

#### Version 2 (with raw VOT)

```{r}

 # calculate entrainment scores (same - different)
entrainment_data$entrainment_ACC <- entrainment_data$mean_ACC_same - entrainment_data$mean_ACC_different
entrainment_data$entrainment_VOT <- (entrainment_data$mean_VOT_same - entrainment_data$mean_VOT_different)

# scatterplot
s <- ggplot(entrainment_data, aes(x=entrainment_VOT, y=entrainment_ACC)) +
  geom_point() +
  stat_smooth(method=lm, fullrange=TRUE, color = 'black') + 
  geom_hline(yintercept=0, linetype="dotted") +
  geom_vline(xintercept=0, linetype="dotted") +
  xlim(-1600, 1600) +
  ylim(-0.5, 0.5) + 
  xlab('Entrainment NL\n(same vs. different)') +
  ylab('Entrainment LM\n(same vs. different)') +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) 
s
ggsave("output_figures/LEALCO-EEG_entrainment_correlation_rawVOT.pdf", width=6, height=3.5)

# correlation
corr <- cor.test(entrainment_data$entrainment_ACC, entrainment_data$entrainment_VOT)
sink('output_stats/LEALCO-EEG_entrainment_correlation_rawVOT.txt')
print(corr)
sink()
```

#### PCA

```{r}

# PCA
pca <- prcomp(entrainment_data[c('entrainment_ACC','entrainment_VOTinv')], center = TRUE, scale = TRUE)
sink('output_stats/LEALCO-EEG_entrainment_pca.txt')
summary(pca)
sink()
 
# add to entrainment dataframe
entrainment_data$PC1 <- pca$x[,'PC1']
entrainment_data$PC2 <- pca$x[,'PC2']

# visualize pca
fviz_eig(pca)

# visualize rotated plot
p8<- ggplot(entrainment_data, aes(x=PC1, y=PC2)) +
  geom_point() +
  geom_smooth(method=lm , se=FALSE, color='black') +
  geom_hline(yintercept=0, linetype="dotted") +
  geom_vline(xintercept=0, linetype="dotted") +
  ylab('PC2') +
  xlab('PC1 / Entrainment') +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) 
p8
ggsave("output_figures/LEALCO-EEG_entrainment_pca_plot.pdf", width=6, height=3.5)

# plot correlation ebtween P200 and PC1
p1<- ggplot(entrainment_data, aes(x=PC1, y=mean_P200_same)) +
  geom_point(color=pal1[1]) +
  geom_smooth(method=lm , color=pal1[1], se=FALSE) +
  geom_point(aes(y=mean_P200_different), color=pal1[2]) +
  geom_smooth(aes(y=mean_P200_different), method=lm , color=pal1[2], se=FALSE) +
  ggtitle("P200")
p1
ggsave("output_figures/LEALCO-EEG_correlation_entrainment_P200.pdf")

# plot correlation ebtween P200 and PC1
p2<- ggplot(entrainment_data, aes(x=PC1, y=mean_P300_same)) +
  geom_point(color=pal1[1]) +
  geom_smooth(method=lm , color=pal1[1], se=FALSE) +
  geom_point(aes(y=mean_P300_different), color=pal1[2]) +
  geom_smooth(aes(y=mean_P300_different), method=lm , color=pal1[2], se=FALSE) +
  ggtitle("P300")
p2
ggsave("output_figures/LEALCO-EEG_correlation_entrainment_P300.pdf")

# save
write.csv(entrainment_data, "output_stats/LEALCO-EEG_entrainment.csv", row.names = FALSE)
```

Examine the simple relationship between accuracy and VOTs separately for the same and different condition. See here to compare two correlations: <https://f-santos.gitlab.io/2020-04-01-comparing-correlation-coefficients.html>

```{r}

# Plot the correlation
p3<- ggplot(entrainment_data, aes(x=mean_VOTinv_same, y=mean_ACC_same)) +
     geom_point(color=pal1[1]) +
     geom_smooth(method=lm , color=pal1[1], se=FALSE) +
     geom_point(aes(x=mean_VOTinv_different, y=mean_ACC_different), color=pal1[2]) +
     geom_smooth(aes(x=mean_VOTinv_different, y=mean_ACC_different), method=lm , color=pal1[2], se=FALSE) +
     xlab('Naming Latencies (inverted)') +
     ylab('Label Maintenance') 
 p3
 ggsave("output_figures/LEALCO-EEG_correlation_behavioral.pdf")
 
# make separate correlations for same and differet
cor_same <- cor.test(entrainment_data$mean_VOTinv_same, entrainment_data$mean_ACC_same)
cor_diff <- cor.test(entrainment_data$mean_VOTinv_different, entrainment_data$mean_ACC_different)
sink('output_stats/LEALCO-EEG_correlation_behavior.txt')
print(cor_same)
print(cor_diff)
sink()
 
#cocor(~ mean_VOTinv_same + mean_ACC_same | mean_VOTinv_different + mean_ACC_different, data = entrainment_data, test = c("silver2004", "zou2007"))
```

#### LMM on P200

Prepara data for LMM.

```{r}
# add the PC1 data to the trial-by-trial P200 data
P200 <- merge(x = P200, y = entrainment_data[c('subjID', 'PC1', 'entrainment_VOTinv', 'entrainment_VOT', 'entrainment_ACC')], by = "subjID", all.x = TRUE)

# center PC1
P200 <- P200 %>%
  mutate(c_PC1 = PC1 - mean(PC1, na.rm=TRUE),
         c_entrainment_VOTinv = entrainment_VOTinv - mean(entrainment_VOTinv, na.rm=TRUE),
         c_entrainment_VOT = entrainment_VOT - mean(entrainment_VOT, na.rm=TRUE),
         c_entrainment_ACC = entrainment_ACC - mean(entrainment_ACC, na.rm=TRUE)
         )
```

##### P200 \~ entrainment VOTinv

```{r}
# indicate the maximal effect structutre (both fixed and random) that is motivated based on design & hypotheses
f <- P200 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * entrainment_VOTinv +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness*entrainment_VOTinv | subjID) +
     (partner_type*block*entrainment_VOTinv | target_label)

# select the maximal model that still converges
m_P200_entr_VOTinv <- buildmer(f,data=P200,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P200_entr_VOTinv)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P200entrainment_LMM_VOTinv.txt")
summary(m_P200_entr_VOTinv)
sink(file = NULL)

save_model_to_html(m_P200_entr_VOTinv@model, 3, "LEALCO-EEG_P200entrainment_LMM_VOTinv.html")
```

##### \>Follow-up: Patner Type x entrainment_VOTinv

```{r}
# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P200_entr_VOTinv@model, pairwise ~ partner_type * entrainment_VOTinv, adjust ="Tukey",, cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P200_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P200_ph_tukey,"output_stats/LEALCO-EEG_P200entrainment_ph_tukey_partner_x_entrVOTinv.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P200_entr_VOTinv@model, pairwise ~ partner_type * entrainment_VOTinv, adjust = "none", , cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P200_ph_none <- as.data.frame(emm_none$contrasts)
P200_ph_none$Bonf2 <- P200_ph_none$p.value * 2
P200_ph_none$Bonf3 <- P200_ph_none$p.value * 3
write.csv(P200_ph_none,"output_stats/LEALCO-EEG_P200entrainment_ph_none_partner_x_entrVOTinv.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(entrainment_VOTinv=c(min(P200$entrainment_VOTinv), median(P200$entrainment_VOTinv), max(P200$entrainment_VOTinv)),
                partner_type=c("same","different")))
P200_marginalMeans <- emmip(m_P200_entr_VOTinv@model, partner_type  ~ entrainment_VOTinv, at=mylist,CIs=TRUE, plotit=TRUE)
write.csv(P200_marginalMeans$data,"output_stats/LEALCO-EEG_P200entrainment_marginalMeans_partner_x_entrVOTinv.csv", row.names = FALSE)

#P200_marginalMeans$data$entrainment_VOTinv <- P200_marginalMeans$data$entrainment_VOTinv - mean(P200$PC1)

# plot 
p1 <- ggplot(P200_marginalMeans$data, aes(x=entrainment_VOTinv, y=yvar, color=partner_type, group=partner_type)) +
  geom_point(stat = "identity", position=position_dodge(0.9)) +
  geom_errorbar(aes(ymin=yvar-SE, ymax=yvar+SE), width=.3, position=position_dodge(0.9)) +
  #geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  #facet_grid(cols = "PC1") +
  labs(y="P200 (\u00b5V)", x="Part.-Spec. Naming Latency") +
  ylim(-4, 14) +
  xlim(-3, 3) +
  geom_hline(yintercept=0, linetype=3) +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) 
p1
ggsave("output_figures/LEALCO-EEG_P200entrainment_partner_x_entrVOTinv.pdf", width=4, height=3)
```

##### \>Folow-up: Patner Type x Image Agreement

```{r}
# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P200_entr_VOTinv@model, pairwise ~ partner_type * c_FASQUEL_image_agreement, adjust ="Tukey",, cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P200_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P200_ph_tukey,"output_stats/LEALCO-EEG_P200entrainment_ph_tukey_partner_x_imageagreement.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P200_entr_VOTinv@model, pairwise ~ partner_type * c_FASQUEL_image_agreement, adjust = "none", , cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P200_ph_none <- as.data.frame(emm_none$contrasts)
P200_ph_none$Bonf2 <- P200_ph_none$p.value * 2
P200_ph_none$Bonf3 <- P200_ph_none$p.value * 3
write.csv(P200_ph_none,"output_stats/LEALCO-EEG_P200entrainment_ph_none_partner_x_imageagreement.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(c_FASQUEL_image_agreement=c(min(P200$c_FASQUEL_image_agreement), median(P200$c_FASQUEL_image_agreement), max(P200$c_FASQUEL_image_agreement)),
                partner_type=c("same","different")))
P200_marginalMeans <- emmip(m_P200_entr_VOTinv@model, partner_type  ~ c_FASQUEL_image_agreement, at=mylist,CIs=TRUE, plotit=TRUE)

# plot
p1 <- ggplot(P200_marginalMeans$data, aes(x=c_FASQUEL_image_agreement, y=yvar, color=partner_type, group=partner_type)) +
  geom_point(stat = "identity", position=position_dodge(0.3)) +
  geom_errorbar(aes(ymin=yvar-SE, ymax=yvar+SE), width=.2, position=position_dodge(0.3)) +
  #geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  #facet_grid(cols = "PC1") +
  labs(y="P200 (\u00b5V)", x="Image Agreement (centered)") +
  ylim(-4, 20) +
  geom_hline(yintercept=0, linetype=3) +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) 
p1
ggsave("output_figures/LEALCO-EEG_P200entrainment_partner_x_imageagreement.pdf", width=5, height=4)

# or alternatively plot like this:
# b <- plot_model(P300@model,
#                 type = "pred",
#                 terms = c("c_FASQUEL_image_agreement [all]","partner_type"), colors = pal1, mdrt.values = c("all"), se=TRUE)
```

##### \>Follow up: Partner Type x entrainment_VOTinv x Frequency

```{r}

# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P200_entr_VOTinv@model, pairwise ~ partner_type * entrainment_VOTinv * c_SUBTLEX_frequency_log, adjust ="Tukey", cov.reduce = function(x) quantile(x, c(0, 0.5,  1)))
P200_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P200_ph_tukey,"output_stats/LEALCO-EEG_P200entrainment_ph_tukey_partner_x_entrVOTinv_x_frequency.csv", row.names = FALSE)

# make post-hoc without correction
emm_none <-emmeans(m_P200_entr_VOTinv@model, pairwise ~ partner_type * entrainment_VOTinv * c_SUBTLEX_frequency_log, adjust ="none", cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P200_ph_none <- as.data.frame(emm_none$contrasts)
write.csv(P200_ph_none,"output_stats/LEALCO-EEG_P200entrainment_ph_none_partner_x_entrVOTinv_x_frequency.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(entrainment_VOTinv=c(min(P200$entrainment_VOTinv),median(P200$entrainment_VOTinv), max(P200$entrainment_VOTinv)),
                c_SUBTLEX_frequency_log=c(min(P200$c_SUBTLEX_frequency_log), median (P200$c_SUBTLEX_frequency_log), max(P200$c_SUBTLEX_frequency_log)),
                partner_type=c("same","different")))
P200_marginalMeans <- emmip(m_P200_entr_VOTinv@model, c_SUBTLEX_frequency_log ~ partner_type  ~ entrainment_VOTinv, at=mylist,CIs=TRUE, plotit=TRUE)

# plot
p <- ggplot(P200_marginalMeans$data, aes(x=partner_type, y=yvar, color=partner_type, group=c_SUBTLEX_frequency_log)) +
  geom_point(stat = "identity") +
  geom_errorbar(aes(ymin=yvar-SE, ymax=yvar+SE), width=.2, position=position_dodge(0.9)) +
  #geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  facet_grid(c_SUBTLEX_frequency_log ~ entrainment_VOTinv) +
  labs(y="P200 (\u00b5V)", x="Entrainment NL (centered)") +
  ylim(-4, 20) +
  geom_hline(yintercept=0, linetype=3) +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) 
p
ggsave("output_figures/LEALCO-EEG_P200entrainment_partner_x_entrVOTinv_x_frequency.pdf")
```

##### P200 \~ entrainment_VOT

```{r}
# indicate the maximal effect structutre (both fixed and random) that is motivated based on design & hypotheses
f <- P200 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * entrainment_VOT +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness*entrainment_VOT | subjID) +
     (partner_type*block*entrainment_VOT | target_label)

# select the maximal model that still converges
m_P200_entr_VOT <- buildmer(f,data=P200,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P200_entr_VOT)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P200entrainment_LMM_VOT.txt")
summary(m_P200_entr_VOT)
sink(file = NULL)

save_model_to_html(m_P200_entr_VOT@model, 3, "LEALCO-EEG_P200entrainment_LMM_VOT.html")
```

##### \>Follow-up: Patner Type x entrainment_VOT

```{r}
# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P200_entr_VOT@model, pairwise ~ partner_type * entrainment_VOT, adjust ="Tukey",, cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P200_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P200_ph_tukey,"output_stats/LEALCO-EEG_P200entrainment_ph_tukey_partner_x_entrVOT.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P200_entr_VOT@model, pairwise ~ partner_type * entrainment_VOT, adjust = "none", , cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P200_ph_none <- as.data.frame(emm_none$contrasts)
P200_ph_none$Bonf2 <- P200_ph_none$p.value * 2
P200_ph_none$Bonf3 <- P200_ph_none$p.value * 3
write.csv(P200_ph_none,"output_stats/LEALCO-EEG_P200entrainment_ph_none_partner_x_entrVOT.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(entrainment_VOT=c(min(P200$entrainment_VOT), median(P200$entrainment_VOT), max(P200$entrainment_VOT)),
                partner_type=c("same","different")))
P200_marginalMeans <- emmip(m_P200_entr_VOT@model, partner_type  ~ entrainment_VOT, at=mylist,CIs=TRUE, plotit=TRUE)
write.csv(P200_marginalMeans$data,"output_stats/LEALCO-EEG_P200entrainment_marginalMeans_partner_x_entrVOT.csv", row.names = FALSE)

#P200_marginalMeans$data$entrainment_VOTinv <- P200_marginalMeans$data$entrainment_VOTinv - mean(P200$PC1)

# plot 
p1 <- ggplot(P200_marginalMeans$data, aes(x=entrainment_VOT, y=yvar, color=partner_type, group=partner_type)) +
  geom_point(stat = "identity", position=position_dodge(200)) +
  geom_errorbar(aes(ymin=yvar-SE, ymax=yvar+SE), width=100, position=position_dodge(200)) +
  #geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  #facet_grid(cols = "PC1") +
  labs(y="P200 (\u00b5V)", x="Entrainment NL") +
  ylim(-4, 14) +
  #xlim(-3, 3) +
  geom_hline(yintercept=0, linetype=3) +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) 
p1
ggsave("output_figures/LEALCO-EEG_P200entrainment_partner_x_entrVOT.pdf", width=4, height=3)
```

##### P200 \~ entrainment_ACC

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P200 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * c_entrainment_ACC +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness*entrainment_VOTinv | subjID) +
     (partner_type*block*entrainment_VOTinv | target_label)

# select the maximal model that still converges
m_P200_entr_acc <- buildmer(f,data=P200,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P200_entr_acc)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P200entrainment_LMM_acc.txt")
summary(m_P200_entr_acc)
sink(file = NULL)

save_model_to_html(m_P200_entr_acc@model, 3, "LEALCO-EEG_P200entrainment_LMM_acc.html")
```

##### \>Follow-up: Patner Type x entrainment_ACC

```{r}
# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P200_entr_acc@model, pairwise ~ partner_type * c_entrainment_ACC, adjust ="Tukey",, cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P200_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P200_ph_tukey,"output_stats/LEALCO-EEG_P200entrainment_ph_tukey_partner_x_entrACC.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P200_entr_acc@model, pairwise ~ partner_type * c_entrainment_ACC, adjust = "none", , cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P200_ph_none <- as.data.frame(emm_none$contrasts)
P200_ph_none$Bonf2 <- P200_ph_none$p.value * 2
P200_ph_none$Bonf3 <- P200_ph_none$p.value * 3
write.csv(P200_ph_none,"output_stats/LEALCO-EEG_P200entrainment_ph_none_partner_x_entrACC.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(c_entrainment_ACC=c(min(P200$c_entrainment_ACC), median(P200$c_entrainment_ACC), max(P200$c_entrainment_ACC)),
                partner_type=c("same","different")))
P200_marginalMeans <- emmip(m_P200_entr_acc@model, partner_type  ~ c_entrainment_ACC, at=mylist,CIs=TRUE, plotit=TRUE)
write.csv(P200_marginalMeans$data,"output_stats/LEALCO-EEG_P200entrainment_marginalMeans_partner_x_entrACC.csv", row.names = FALSE)

#P200_marginalMeans$data$entrainment_VOTinv <- P200_marginalMeans$data$entrainment_VOTinv - mean(P200$PC1)

# plot 
p1 <- ggplot(P200_marginalMeans$data, aes(x=c_entrainment_ACC, y=yvar, color=partner_type, group=partner_type)) +
  geom_point(stat = "identity", position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=yvar-SE, ymax=yvar+SE), width=.1, position=position_dodge(0.1)) +
  #geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  #facet_grid(cols = "PC1") +
  labs(y="P200 (\u00b5V)", x="Entrainment LM") +
  ylim(-4, 14) +
  xlim(-0.5, 0.5) +
  geom_hline(yintercept=0, linetype=3) +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) 
p1
ggsave("output_figures/LEALCO-EEG_P200entrainment_partner_x_entrACC.pdf", width=4, height=3)
```

#### LMM on 200 with offset

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P200 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * entrainment_VOTinv * c_offset +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness*entrainment_VOTinv* c_offset | subjID) +
     (partner_type*block*entrainment_VOTinv* c_offset | target_label)

# select the maximal model that still converges
m_P200_offset_entr <- buildmer(f,data=P200,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P200_offset_entr)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P200_offset_entrainment_LMM.txt")
summary(m_P200_offset_entr)
sink(file = NULL)
```

#### LMM on P300

Prepara data for LMM.

```{r}
# add the PC1 data to the trial-by-trial P200 data
P300 <- merge(x = P300, y = entrainment_data[c('subjID', 'PC1', 'entrainment_VOTinv', 'entrainment_VOT', 'entrainment_ACC')], by = "subjID", all.x = TRUE)

# center PC1
P300 <- P300 %>%
  mutate(c_PC1 = PC1 - mean(PC1, na.rm=TRUE),
         c_entrainment_VOTinv = entrainment_VOTinv - mean(entrainment_VOTinv, na.rm=TRUE),
         c_entrainment_VOT = entrainment_VOT - mean(entrainment_VOT, na.rm=TRUE),
         c_entrainment_ACC = entrainment_ACC - mean(entrainment_ACC, na.rm=TRUE)
         )
```

##### P300 \~ entrainment VOTinv

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P300 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * entrainment_VOTinv +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness*entrainment_VOTinv | subjID) +
     (partner_type*block*entrainment_VOTinv | target_label)

# select the maximal model that still converges
m_P300_entr_VOTinv <- buildmer(f,data=P300,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P300_entr_VOTinv)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P300entrainment_LMM_entrVOTinv.txt")
summary(m_P300_entr_VOTinv)
sink(file = NULL)

save_model_to_html(m_P300_entr_VOTinv@model, 3, "LEALCO-EEG_P300entrainment_LMM_VOTinv.html")
```

##### \>Follow-up: Patner Type x entrainment_VOTinv

```{r}
# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P300_entr_VOTinv@model, pairwise ~ partner_type * entrainment_VOTinv, adjust ="Tukey",, cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P300_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P300_ph_tukey,"output_stats/LEALCO-EEG_P300entrainment_ph_tukey_partner_x_entrVOTinv.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P300_entr_VOTinv@model, pairwise ~ partner_type * entrainment_VOTinv, adjust = "none", , cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P300_ph_none <- as.data.frame(emm_none$contrasts)
P300_ph_none$Bonf2 <- P300_ph_none$p.value * 2
P300_ph_none$Bonf3 <- P300_ph_none$p.value * 3
write.csv(P300_ph_none,"output_stats/LEALCO-EEG_P300entrainment_ph_none_partner_x_entrVOTinv.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(entrainment_VOTinv=c(min(P300$entrainment_VOTinv), median(P300$entrainment_VOTinv), max(P300$entrainment_VOTinv)),
                partner_type=c("same","different")))
P300_marginalMeans <- emmip(m_P300_entr_VOTinv@model, partner_type  ~ entrainment_VOTinv, at=mylist,CIs=TRUE, plotit=TRUE)
write.csv(P300_marginalMeans$data,"output_stats/LEALCO-EEG_P300entrainment_marginalMeans_partner_x_entrVOTinv.csv", row.names = FALSE)

# plot 
p1 <- ggplot(P300_marginalMeans$data, aes(x=entrainment_VOTinv, y=yvar, color=partner_type, group=partner_type)) +
  geom_point(stat = "identity", position=position_dodge(0.9)) +
  geom_errorbar(aes(ymin=yvar-SE, ymax=yvar+SE), width=.3, position=position_dodge(0.9)) +
  #geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  #facet_grid(cols = "PC1") +
  labs(y="P300 (\u00b5V)", x="Part.-Spec. Naming Latency") +
  ylim(-4, 14) +
  xlim(-3, 3) +
  geom_hline(yintercept=0, linetype=3) +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) 
p1
ggsave("output_figures/LEALCO-EEG_P300entrainment_partner_x_entrVOTinv.pdf", width=4, height=3)
```

##### \>Follow-up: Patner Type x Block

```{r}
# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P300_entr@model, pairwise ~ partner_type * block, adjust ="Tukey")
P300_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P300_ph_tukey,"output_stats/LEALCO-EEG_P300entrainment_ph_tukey_partner_x_block.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P300_entr@model, pairwise ~ partner_type * block, adjust = "none")
P300_ph_none <- as.data.frame(emm_none$contrasts)
P300_ph_none$Bonf2 <- P300_ph_none$p.value * 2
write.csv(P300_ph_none,"output_stats/LEALCO-EEG_P300entrainment_ph_none_partner_x_block.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(block=c("1", "2"),
                partner_type=c("same","different")))
P300_marginalMeans <- emmip(m_P300_entr@model, partner_type  ~ block, at=mylist,CIs=TRUE, plotit=TRUE)

# plot
p <- ggplot(P300_marginalMeans$data, aes(x=block, y=yvar, color=partner_type, group=partner_type)) +
  geom_point(stat = "identity", position=position_dodge(0.9)) +
  geom_errorbar(aes(ymin=yvar-SE, ymax=yvar+SE), width=.2, position=position_dodge(0.9)) +
  #geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  #facet_grid(cols = "PC1") +
  labs(y="P300 (\u00b5V)", x="Block") +
  ylim(-4, 20) +
  geom_hline(yintercept=0, linetype=3) +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16))
p
ggsave("output_figures/LEALCO-EEG_P300entrainment_partner_x_block.pdf", width=5, height=4)
```

##### P300 \~ entrainment_VOT

```{r}
# indicate the maximal effect structutre (both fixed and random) that is motivated based on design & hypotheses
f <- P300 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * entrainment_VOT +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness*entrainment_VOT | subjID) +
     (partner_type*block*entrainment_VOT | target_label)

# select the maximal model that still converges
m_P300_entr_VOT <- buildmer(f,data=P300,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P300_entr_VOT)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P300entrainment_LMM_VOT.txt")
summary(m_P300_entr_VOT)
sink(file = NULL)

save_model_to_html(m_P300_entr_VOT@model, 3, "LEALCO-EEG_P300entrainment_LMM_VOT.html")
```

##### \>Follow-up: Patner Type x entrainment_VOT

```{r}
# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P300_entr_VOT@model, pairwise ~ partner_type * entrainment_VOT, adjust ="Tukey",, cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P300_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P300_ph_tukey,"output_stats/LEALCO-EEG_P300entrainment_ph_tukey_partner_x_entrVOT.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P300_entr_VOT@model, pairwise ~ partner_type * entrainment_VOT, adjust = "none", , cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P300_ph_none <- as.data.frame(emm_none$contrasts)
P300_ph_none$Bonf2 <- P300_ph_none$p.value * 2
P300_ph_none$Bonf3 <- P300_ph_none$p.value * 3
write.csv(P300_ph_none,"output_stats/LEALCO-EEG_P300entrainment_ph_none_partner_x_entrVOT.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(entrainment_VOT=c(min(P300$entrainment_VOT), median(P300$entrainment_VOT), max(P300$entrainment_VOT)),
                partner_type=c("same","different")))
P300_marginalMeans <- emmip(m_P300_entr_VOT@model, partner_type  ~ entrainment_VOT, at=mylist,CIs=TRUE, plotit=TRUE)
write.csv(P300_marginalMeans$data,"output_stats/LEALCO-EEG_P300entrainment_marginalMeans_partner_x_entrVOT.csv", row.names = FALSE)

# plot 
p1 <- ggplot(P300_marginalMeans$data, aes(x=entrainment_VOT, y=yvar, color=partner_type, group=partner_type)) +
  geom_point(stat = "identity", position=position_dodge(200)) +
  geom_errorbar(aes(ymin=yvar-SE, ymax=yvar+SE), width=100, position=position_dodge(200)) +
  #geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  #facet_grid(cols = "PC1") +
  labs(y="P300 (\u00b5V)", x="Entrainment NL") +
  ylim(-4, 16) +
  #xlim(-3, 3) +
  geom_hline(yintercept=0, linetype=3) +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) 
p1
ggsave("output_figures/LEALCO-EEG_P300entrainment_partner_x_entrVOT.pdf", width=4, height=3)
```

##### P300 \~ entrainment_ACC

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P300 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * c_entrainment_ACC +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness*entrainment_VOTinv | subjID) +
     (partner_type*block*entrainment_VOTinv | target_label)

# select the maximal model that still converges
m_P300_entr_acc <- buildmer(f,data=P200,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P300_entr_acc)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P300entrainment_LMM_acc.txt")
summary(m_P300_entr_acc)
sink(file = NULL)

save_model_to_html(m_P300_entr_acc@model, 3, "LEALCO-EEG_P300entrainment_LMM_acc.html")
```

##### \>Follow-up: Patner Type x entrainment_ACC

```{r}
# make post-hoc with tukey correction
emm_tukey <-emmeans(m_P300_entr_acc@model, pairwise ~ partner_type * c_entrainment_ACC, adjust ="Tukey",, cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P300_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(P300_ph_tukey,"output_stats/LEALCO-EEG_P300entrainment_ph_tukey_partner_x_entrACC.csv", row.names = FALSE)

# make post-hoc with no correction
emm_none <-emmeans(m_P300_entr_acc@model, pairwise ~ partner_type * c_entrainment_ACC, adjust = "none", , cov.reduce = function(x) quantile(x, c(0, 0.5, 1)))
P300_ph_none <- as.data.frame(emm_none$contrasts)
P300_ph_none$Bonf2 <- P300_ph_none$p.value * 2
P300_ph_none$Bonf3 <- P300_ph_none$p.value * 3
write.csv(P300_ph_none,"output_stats/LEALCO-EEG_P300entrainment_ph_none_partner_x_entrACC.csv", row.names = FALSE)

# generate predicted data (but don't plot it yet with emmip)
(mylist <- list(c_entrainment_ACC=c(min(P300$c_entrainment_ACC), median(P300$c_entrainment_ACC), max(P300$c_entrainment_ACC)),
                partner_type=c("same","different")))
P300_marginalMeans <- emmip(m_P300_entr_acc@model, partner_type  ~ c_entrainment_ACC, at=mylist,CIs=TRUE, plotit=TRUE)
write.csv(P300_marginalMeans$data,"output_stats/LEALCO-EEG_P300entrainment_marginalMeans_partner_x_entrACC.csv", row.names = FALSE)

# plot 
p1 <- ggplot(P300_marginalMeans$data, aes(x=c_entrainment_ACC, y=yvar, color=partner_type, group=partner_type)) +
  geom_point(stat = "identity", position=position_dodge(0.1)) +
  geom_errorbar(aes(ymin=yvar-SE, ymax=yvar+SE), width=.1, position=position_dodge(0.1)) +
  #geom_ribbon(aes(ymin=LCL, ymax=UCL, fill=partner_type), alpha=.5) +
  scale_fill_manual(values = pal1) +
  scale_color_manual(values = pal1) +
  #facet_grid(cols = "PC1") +
  labs(y="P300 (\u00b5V)", x="Entrainment LM") +
  ylim(-4, 15) +
  xlim(-0.5, 0.5) +
  geom_hline(yintercept=0, linetype=3) +
  theme(axis.text=element_text(size=15), axis.title=element_text(size=16)) 
p1
ggsave("output_figures/LEALCO-EEG_P300entrainment_partner_x_entrACC.pdf", width=4, height=3)
```

#### LMM on P300 with offset

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P300 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness * m_P300_entr * c_offset +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness*m_P300_entr* c_offset | subjID) +
     (partner_type*block*m_P300_entr* c_offset | target_label)

# select the maximal model that still converges
m_P300_offset_entr <- buildmer(f,data=P300,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P300_offset_entr)

# save winning model
sink(file = "output_stats/LEALCO-EEG_P300_offset_entrainment_LMM.txt")
summary(m_P300_offset_entr)
sink(file = NULL)
```

## ERROR PATTERN AT INCORRECT TRIALS

### By Subject (native, partner x block)

First, we need to dummy code our *error* variable so that from an *error* variable with 4 levels, we get four variables (one per error type) with a binary outcome each. This will make it easier to calculate rates for each error type as well as run LMM later.

```{r}
# make dummy coding
data_trained$error_1 <- ifelse(data_trained$error == 1, 1, 0)
data_trained$error_2 <- ifelse(data_trained$error == 2, 1, 0)
data_trained$error_3 <- ifelse(data_trained$error == 3, 1, 0)
data_trained$error_4 <- ifelse(data_trained$error == 4, 1, 0)
```

```{r}
# aggregte (within subject)
error_acc_wSubj_partner <- data_trained %>%
  filter(!subjID %in%  c(exclusion_acc, 33))  %>%
  group_by(subjID, partner_type, block) %>%
  summarise(compound = mean(error_1),
            semantically_related = mean(error_2),
            phonologically_related = mean(error_3),
            unrelated = mean(error_4))

# pivot
error_acc_wSubj_partner <-error_acc_wSubj_partner %>% 
  pivot_longer(
    cols = !c(subjID, partner_type, block), 
    names_to = "error", 
    values_to = "rate"
  )

# save
write.csv(error_acc_wSubj_partner, "output_stats/LEALCO-EEG_error_acc_withinSubjects_partner.csv", row.names = FALSE)

error_acc_bSubj_partner <- error_acc_wSubj_partner %>%
  group_by(partner_type, block, error) %>%
  summarise(mean_bSubj = mean(rate), sd_bSubj=sd(rate), sem_bSubj=(sd(rate)/sqrt((length(rate)))), n_bSubj=length(rate))

# save
write.csv(error_acc_bSubj_partner, "output_stats/LEALCO-EEG_error_acc_betweenSubjects_partner.csv", row.names = FALSE)
```

```{r}

# plot (within subject)
pdf("output_figures/LEALCO-EEG_error_acc_betweenSubjects_partner_block_barplot.pdf")
c <- ggplot(error_acc_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  scale_fill_manual(values = pal1) +
  labs(y="Average error rate", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA) +
  facet_grid(error ~ block)
c
dev.off()
c

# make other more transparent plot
pdf("output_figures/LEALCO-EEG_error_acc_betweenSubjects_partner_block_pointplot.pdf")
zz <- ggplot(error_acc_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_point(data= error_acc_wSubj_partner, aes(y=rate, x=partner_type, color=partner_type), stat="identity", position = position_jitter(w = 0.05), size=0.8) + 
  scale_colour_manual(values = pal1) +
    geom_point(stat="identity", color = "black", position=position_dodge(), size=2) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Average error rate", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1) +
  facet_grid(error ~ block)
zz
dev.off()
```

### LMM

```{r}
# select data
error_acc <- data_trained %>%
  #filter(error %in% c(1, 2, 3, 4)) %>%
  filter(!subjID %in%  c(exclusion_acc, 33))

# Set sum contrasts for all variables.
error_acc$partner_type <- droplevels(error_acc$partner_type)
contrasts(error_acc$partner_type) <- contr.sum(2)
contrasts(error_acc$block)  <- contr.sum(2)

# check contrasts
contrasts(error_acc$partner_type)
contrasts(error_acc$block)

# center covariates
error_acc <- error_acc %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

error_acc <- error_acc %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

error_acc <- error_acc %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

error_acc <- error_acc %>%
  mutate(team = team - mean(team, na.rm=TRUE))
```

#### 1 - compound words

```{r}

# define maximal model structure
f <-  error_1 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
     (partner_type*block | target_label)

# fit model
m_error_acc_1 <- buildmer(f,family=binomial,data=error_acc,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_error_acc_1)

# save winning model
sink(file = "output_stats/LEALCO-EEG_error_acc_LMM_1.txt")
summary(m_error_acc_1)
sink(file = NULL)
```

#### 2 - semantically related words

```{r}
# define maximal model structure
f <-  error_2 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
     (partner_type*block | target_label)

# fit model
m_error_acc_2 <- buildmer(f,family=binomial, data=error_acc,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_error_acc_2)

# save winning model
sink(file = "output_stats/LEALCO-EEG_error_acc_LMM_2.txt")
summary(m_error_acc_2)
sink(file = NULL)
```

#### 4 - unrelated words

```{r}
# define maximal model structure
f <-  error_4 ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
     (partner_type*block | target_label)

# fit model
m_error_acc_4 <- buildmer(f,family=binomial, data=error_acc,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_error_acc_4)

# save winning model
sink(file = "output_stats/LEALCO-EEG_error_acc_LMM_4.txt")
summary(m_error_acc_4)
sink(file = NULL)
```

## NAMING LATENCIES AT INACCURATE TRIALS

### By Subject (native, partner x block)

```{r}
# aggregte (within subject)
error_vot_wSubj_partner <- data_trained %>%
  filter(error %in% c(1,2,3,4)) %>%
  filter(!subjID %in%  c(exclusion_vot, 33))  %>%
  group_by(subjID, partner_type, block, error) %>%
  summarise(mean = mean(VOT), sd=sd(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), n=length(VOT))

# rename the errors (for better graph legibility)
error_vot_wSubj_partner$error <- recode(error_vot_wSubj_partner$error,
                                       '1' = 'compound', 
                                       '2' = 'semantically_related',
                                       '3' = 'phonologically_related',
                                       '4' = 'unrelated')

# save
write.csv(vot_wSubj_partner, "output_stats/LEALCO-EEG_error_vot_withinSubjects_partner_block.csv", row.names = FALSE)

error_vot_bSubj_partner <- error_vot_wSubj_partner %>%
  group_by(partner_type, block, error) %>%
  summarise(mean_bSubj = mean(mean), sd_bSubj=sd(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))), n_bSubj=length(mean))

# save
write.csv(acc_bSubj_partner, "output_stats/LEALCO-EEG_error_accuracy_betweenSubjects_partner_block.csv", row.names = FALSE)

```

```{r}

# reorder the factor levels (so that they are shown in the right order in the plot)
error_vot_bSubj_partner$error <- factor(error_vot_bSubj_partner$error, levels = c("correct", "compound", "semantically_related", "phonologically_related", "unrelated", "5", "6", "8", "9", "0"))

# plot (within subject)
pdf("output_figures/LEALCO-EEG_error_vot_betweenSubjects_partner_block_barplot.pdf")
c <- ggplot(error_vot_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  scale_fill_manual(values = pal1) +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA) +
  facet_grid(error ~ block)
c
dev.off()
c

# make other more transparent plot
pdf("output_figures/LEALCO-EEG_error_vot_betweenSubjects_partner_block_pointplot.pdf")
zz <- ggplot(error_vot_bSubj_partner, aes(y=mean_bSubj, x=partner_type, fill=partner_type)) + 
  geom_point(data= error_vot_wSubj_partner, aes(y=mean, x=partner_type, color=partner_type), stat="identity", position = position_jitter(w = 0.05), size=1) + 
  scale_colour_manual(values = pal1) +
    geom_point(stat="identity", color = "black", position=position_dodge(), size=2) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA) +
  facet_grid(error ~ block)
zz
dev.off()
zz
```

### LMM

First select all error trials

```{r}
# select data
error_votINV <- data_trained %>%
  filter(error %in% c(1, 2, 3, 4)) %>%
  filter(!subjID %in%  c(exclusion_vot, 33))

# Set sum contrasts for all variables.
error_votINV$partner_type <- droplevels(error_votINV$partner_type)
contrasts(error_votINV$partner_type) <- contr.sum(2)
contrasts(error_votINV$block)  <- contr.sum(2)

# check contrasts
contrasts(error_votINV$partner_type)
contrasts(error_votINV$block)

# center covariates
error_votINV <- error_votINV %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

error_votINV <- error_votINV %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

error_votINV <- error_votINV %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

error_votINV <- error_votINV %>%
  mutate(team = team - mean(team, na.rm=TRUE))
```

Indicate the maximal effect structure (both fixed and random) that is motivated based on design & hypotheses.

```{r}
f <- VOTinv ~ partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (partner_type*block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
     (partner_type*block | target_label)

```

#### 1- compound words

```{r}

error_votINV_1 <- error_votINV %>%
  filter (error == 1)
m_error_votINV_1 <- buildmer(f,data=error_votINV_1,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_error_votINV_1)

# save winning model
sink(file = "output_stats/LEALCO-EEG_error_votINV_LMM_1.txt")
summary(m_error_votINV_1)
sink(file = NULL)
```

#### 2 - semantically related errors

```{r}

error_votINV_2 <- error_votINV %>%
  filter (error == 2)
m_error_votINV_2 <- buildmer(f,data=error_votINV_2,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_error_votINV_2)

# save winning model
sink(file = "output_stats/LEALCO-EEG_error_votINV_LMM_2.txt")
summary(m_error_votINV_2)
sink(file = NULL)
```

#### 4 - unrelated erros

```{r}

error_votINV_4 <- error_votINV %>%
  filter (error == 4)
m_error_votINV_4 <- buildmer(f,data=error_votINV_4,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_error_votINV_4)

# save winning model
sink(file = "output_stats/LEALCO-EEG_error_votINV_LMM_4.txt")
summary(m_error_votINV_4)
sink(file = NULL)
```

# == Untrained trials ==

```{r}
data_untrained <- data %>%
  filter(class == 'untrained') %>%
  filter(error %in% c('correct', '1', '2', '3', '4'))
```

## ACCURACY

### By Subject (frequency x block)

```{r}
# aggregte (within subject)
acc_wSubj <- data_untrained %>%
  filter(!subjID %in%  exclusion_acc) %>%
  group_by(subjID, SUBTLEX_frequency_log_cat, block) %>%
  summarise(mean = mean(correct), sem=(sd(correct)/sqrt((length(correct)))))

# plot (within subject)
pdf("output_figures/LEALCO-EEG_untrained_accuracy_withinSubjects_partner_x_block.pdf")
a <- ggplot(acc_wSubj, aes(y=mean, x=block, fill=SUBTLEX_frequency_log_cat)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal2) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
  labs(y="Accuracy (proportion)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}
# aggregte (between subject)
acc_bSubj <- acc_wSubj %>%
  group_by(SUBTLEX_frequency_log_cat,block) %>%
  summarise(mean_bSubj = mean(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))))

# plot (within subject)
pdf("output_figures/LEALCO-EEG_untrained_accuracy_betweenSubjects_partner_x_block.pdf")
c <- ggplot(acc_bSubj, aes(y=mean_bSubj, x=block, fill=SUBTLEX_frequency_log_cat)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal2) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Accuracy (proportion)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,1)
c
dev.off()
c
```

## NAMING LATENCIES AT ACCURATE TRIALS

### By Subjects (native, frequency x block)

```{r}
# aggregte (within subject)
VOT_wSubj <- data_untrained %>%
  filter(!subjID %in%  exclusion_vot) %>%
  filter(correct == 1) %>%
  group_by(subjID, SUBTLEX_frequency_log_cat, block) %>%
  summarise(mean = mean(VOT), sem=(sd(VOT)/sqrt((length(VOT)))))

# plot (within subject)
pdf("output_figures/LEALCO-EEG_untrained_vot_withinSubjects_frequency_x_block_barplot.pdf")
a <- ggplot(VOT_wSubj, aes(y=mean, x=block, fill=SUBTLEX_frequency_log_cat)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal2) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
      labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA) +
  facet_wrap(~subjID)
a
dev.off()
a
```

```{r}

# aggregte (between subject)
VOT_bSubj <- VOT_wSubj %>%
  group_by(SUBTLEX_frequency_log_cat,block) %>%
  summarise(mean_bSubj = mean(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))))

# barplotplot (between subject)
pdf("output_figures/LEALCO-EEG_untrained_vot_betweenSubjects_frequency_x_block_barplot.pdf")
c <- ggplot(VOT_bSubj, aes(y=mean_bSubj, x=block, fill=SUBTLEX_frequency_log_cat)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal2) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
    labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA)
c
dev.off()
c 

# pointplot plot (between subjects)
pdf("output_figures/LEALCO-EEG_untrained_vot_betweenSubjects_frequency_x_block_pointplot.pdf")
tt <- ggplot(VOT_bSubj, aes(y=mean_bSubj, x=block, fill=SUBTLEX_frequency_log_cat)) + 
  geom_point(data= VOT_wSubj, aes(y=mean, x=block, color=SUBTLEX_frequency_log_cat), stat="identity", position = position_jitterdodge(jitter.w = 0.05, dodge.width=(.9)), size=3) +
  scale_colour_manual(values = pal2) +
  geom_point(stat="identity", color = "black", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

### By Subjects (native, image agreement x block)

It becomes clear from the item analysis that our initial distinction between HF and LF items was heavily confounded with image agreement (and possibly concreteness, which highly correlated with image agreement), Therefore, we here regroup the stimuli based on image agreement, rather than frequency.

Note however that this approach comes with problems. The high and low image agreement stimuli are not necessarily matched for other variables any longer.

```{r}
# find median
med <- median(data_untrained$FASQUEL_image_agreement)

# make median split
 data_untrained$FASQUEL_image_agreement_cat <- ifelse(data_untrained$FASQUEL_image_agreement < med, 'LIA', 'HIA')
 data_untrained$FASQUEL_image_agreement_cat <- as_factor( data_untrained$FASQUEL_image_agreement_cat)
```

```{r}
# aggregte (within subject)
VOT_wSubj_IA <- data_untrained %>%
  filter(!subjID %in%  exclusion_vot) %>%
  filter(correct == 1) %>%
  group_by(subjID, FASQUEL_image_agreement_cat, block) %>%
  summarise(mean = mean(VOT), sem=(sd(VOT)/sqrt((length(VOT)))))

# plot (within subject)
pdf("output_figures/LEALCO-EEG_untrained_vot_IA_withinSubjects_imageAgreement_x_block_barplot.pdf")
a <- ggplot(VOT_wSubj_IA, aes(y=mean, x=block, fill=FASQUEL_image_agreement_cat)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal2) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
      labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA) +
  facet_wrap(~subjID)
a
dev.off()
a


```

```{r}
# aggregte (between subject)
VOT_bSubj_IA <- VOT_wSubj_IA %>%
  group_by(FASQUEL_image_agreement_cat,block) %>%
  summarise(mean_bSubj = mean(mean), sem_bSubj=(sd(mean)/sqrt((length(mean)))))

# barplotplot (between subject)
pdf("output_figures/LEALCO-EEG_untrained_vot_IA_betweenSubjects_imageAgreement_x_block_barplot.pdf")
c <- ggplot(VOT_bSubj_IA, aes(y=mean_bSubj, x=block, fill=FASQUEL_image_agreement_cat)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal2) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
    labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA)
c
dev.off()
c

# raincloud plot (between subjects)
pdf("output_figures/LEALCO-EEG_untrained_vot_betweenSubjects_imageAgreement_x_block_pointplot.pdf")
tt <- ggplot(VOT_bSubj_IA, aes(y=mean_bSubj, x=block, fill=FASQUEL_image_agreement_cat)) + 
  geom_point(data= VOT_wSubj_IA, aes(y=mean, x=block, color=FASQUEL_image_agreement_cat), stat="identity", position = position_jitterdodge(jitter.w = 0.05, dodge.width=(.9)), size=3) +
  scale_colour_manual(values = pal2) +
  geom_point(stat="identity", color = "black", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=mean_bSubj-sem_bSubj, ymax=mean_bSubj+sem_bSubj), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

### By Items (frequency x block)

```{r}

# aggregte (within item)
vot_wItem <- data_untrained %>%
  filter(!subjID %in%  exclusion_vot) %>%
  group_by(target_label, block, SUBTLEX_frequency_log_cat) %>%
  summarise(mean = mean(VOT), sem=(sd(VOT)/sqrt((length(VOT)))), logFrequency = mean(SUBTLEX_frequency_log), im_ag = mean(FASQUEL_image_agreement))

# plot (within item)
#pdf("output_figures/LEALCO-EEG_untrained_vot_withinItems_correlation.pdf")
a <- ggplot(vot_wItem, aes(y=mean, x=im_ag, color=block)) + 
  geom_point() +
  stat_smooth(method = "lm", 
              formula = y ~ x, 
              geom = "smooth") 
a
#dev.off()

a <- ggplot(vot_wItem, aes(y=mean, x=logFrequency, color=block)) + 
  geom_point() +
  stat_smooth(method = "lm", 
              formula = y ~ x, 
              geom = "smooth") 
a
```

```{r}
# plot (within item)
pdf("output_figures/LEALCO-EEG_untrained_vot_withinItems_frequency.pdf")
a <- ggplot(vot_wItem, aes(y=mean, x=block, fill=SUBTLEX_frequency_log_cat)) + 
  geom_bar(stat="identity", color = "black", position=position_dodge()) +
  scale_fill_manual(values = pal2) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.2,
                position=position_dodge(.9)) +
  labs(y="Naming latency (ms)", x="Block") +
  theme(axis.text=element_text(size=8), axis.title=element_text(size=16)) +
  facet_wrap(~target_label)
a
dev.off()
a
```

### LMM

Prepare the VOT data for LMMs. Note that we will be running he model on inverted naming latency (1/naming latency). This results in the magnitude of the datapoints being inverted. The estimates of the models have to be read accordingly.

```{r}

# select data
votINV <- data_untrained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_vot)

# change the base level of the Belief and Desire condition to be B+ and D+
#TOM$conditionB <- relevel(TOM$conditionB,  'B+')  
#TOM$conditionD <- relevel(TOM$conditionD, 'D+')  

# Set sum contrasts for all variables.
votINV$SUBTLEX_frequency_log_cat <- droplevels(votINV$SUBTLEX_frequency_log_cat)
contrasts(votINV$SUBTLEX_frequency_log_cat) <- contr.sum(2)
contrasts(votINV$block)  <- contr.sum(2)

# check contrasts
contrasts(votINV$SUBTLEX_frequency_log_cat)
contrasts(votINV$block)

# center covariates
votINV <- votINV %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

votINV <- votINV %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

votINV <- votINV %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

```

Try to find the maximally convergent model by using the *buildmer()* approach.

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- VOTinv ~ SUBTLEX_frequency_log_cat*block* c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (SUBTLEX_frequency_log_cat * block * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
     (block | target_label)

# select the maximal model that still converges
m_votINV <- buildmer(f,data=votINV,buildmerControl=buildmerControl(direction='order',
          args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_votINV)

# save winning model
sink(file = "output_stats/LEALCO-EEG_untrained_votINV_LMM.txt")
summary(m_votINV)
sink(file = NULL)
```

Make model sanity checks. Everything seems ok.

```{r}
# qqplot
pdf("output_figures/LEALCO-EEG_untrained_votINV_lmm_qqplot.pdf")
qqnorm(residuals(m_votINV))
dev.off()

# histogram
pdf("output_figures/LEALCO-EEG_untrained_votINV_lmm_hist.pdf")
hist(residuals(m_votINV))
dev.off()

# standardized residuals
pdf("output_figures/LEALCO-EEG_untrained_votINV_lmm_residuals.pdf")
plot(residuals(m_votINV))
dev.off()
```

#### Follow-up: Frequency x Block x Image Agreement

```{r}

# make post-hoc with tukey correction (frequency x block x image agreement)
emm_tukey <-emmeans(m_votINV@model, pairwise ~ SUBTLEX_frequency_log_cat * c_FASQUEL_concreteness * c_FASQUEL_image_agreement, adjust = "Tukey")
vot_ph_tukey <- as.data.frame(emm_tukey$contrasts)
write.csv(vot_ph_tukey,"output_stats/LEALCO-EEG_untrained_votINV_ph_tukey.csv", row.names = FALSE)

# make post-hoc with no correction (frequency x block  x image agreement)
emm_none <-emmeans(m_votINV@model, pairwise ~ SUBTLEX_frequency_log_cat * block * c_FASQUEL_image_agreement, adjust = "none")
vot_ph_none <- as.data.frame(emm_none$contrasts)
write.csv(vot_ph_none,"output_stats/LEALCO-EEG_untrained_votINV_ph_none.csv", row.names = FALSE)
```

#### Follow-up: Frequency

```{r}
# make post-hoc with no correction (frequency)
emm_none_main <-emmeans(m_votINV@model, pairwise ~ SUBTLEX_frequency_log_cat, adjust = "none")
vot_ph_none_main <- as.data.frame(emm_none_main$contrasts)
write.csv(vot_ph_none_main,"output_stats/LEALCO-EEG_untrained_votINV_ph_none_main.csv", row.names = FALSE)
```

Calculate the marginal means for the main effect of frequency.

```{r}
# extract and save marginal means (frequency)
vot_marginalMeans_main <- as.data.frame(emm_none_main$emmeans)
vot_marginalMeans_main$emmean_untrans <- 1/vot_marginalMeans_main$emmean
vot_marginalMeans_main$lower.CL_untrans <- 1/vot_marginalMeans_main$upper.CL
vot_marginalMeans_main$upper.CL_untrans <- 1/vot_marginalMeans_main$lower.CL
write.csv(vot_marginalMeans_main,"output_stats/LEALCO-EEG_votINV_untrained_lmm_marginal_frequency.csv", row.names = FALSE)

pdf("output_figures/LEALCO-EEG_untrained_votINV_lmm_marginal_frequency_pointplot.pdf")
tt <- ggplot(vot_marginalMeans_main, aes(y=emmean_untrans, x=SUBTLEX_frequency_log_cat, color=SUBTLEX_frequency_log_cat)) + 
  scale_colour_manual(values = pal2) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()
tt
```

#### Follow-up: Partner x Block

```{r}

# extract and save marginal means (partner x block)
vot_marginalMeans <- as.data.frame(emm_tukey$emmeans)
vot_marginalMeans$emmean_untrans <- 1/vot_marginalMeans$emmean
vot_marginalMeans$lower.CL_untrans <- 1/vot_marginalMeans$upper.CL
vot_marginalMeans$upper.CL_untrans <- 1/vot_marginalMeans$lower.CL
write.csv(vot_marginalMeans,"output_stats/LEALCO-EEG_votINV_untrained_lmm_marginal_frequency_x_block.csv", row.names = FALSE)

pdf("output_figures/LEALCO-EEG_untrained_votINV_lmm_marginal_frequency_x_block_pointplot.pdf")
tt <- ggplot(vot_marginalMeans, aes(y=emmean_untrans, x=block, color=SUBTLEX_frequency_log_cat)) + 
  scale_colour_manual(values = pal2) +
  geom_point(stat="identity", position=position_dodge(.9), size=3) +
  geom_errorbar(aes(ymin=lower.CL_untrans, ymax=upper.CL_untrans), width=.2, position=position_dodge(.9)) +
  labs(y="Naming latencies (ms)", x="Block") +
  theme(axis.text=element_text(size=12), axis.title=element_text(size=16)) +
  ylim(0,NA)
tt
dev.off()

```

```{r}
p <- emmip(m_votINV@model, SUBTLEX_frequency_log_cat ~ block ~ c_FASQUEL_image_agreement, cov.reduce = range)
p
```

### P200

```{r}
# select data
P200_untrained <- data_untrained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_eeg)

# change the base level of the Belief and Desire condition to be B+ and D+
#TOM$conditionB <- relevel(TOM$conditionB,  'B+')  
#TOM$conditionD <- relevel(TOM$conditionD, 'D+')  

# Set sum contrasts for all variables.
contrasts(P200_untrained$SUBTLEX_frequency_log_cat) <- contr.sum(2)
contrasts(P200_untrained$block)  <- contr.sum(2)

# check contrasts
contrasts(P200_untrained$SUBTLEX_frequency_log_cat)
contrasts(P200_untrained$block)

# center covariates
P200_untrained <- P200_untrained %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

P200_untrained <- P200_untrained %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

P200_untrained <- P200_untrained %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

P200_untrained <- P200_untrained %>%
  mutate(team = team - mean(team, na.rm=TRUE))
```

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P200 ~ block * SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
     (block | target_label)

# select the maximal model that still converges
m_P200_untrained <- buildmer(f,data=P200_untrained,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P200_untrained)

# save winning model
sink(file = "output_stats/LEALCO-EEG_untrained_P200_LMM.txt")
summary(m_P200_untrained)
sink(file = NULL)
```

### P300

```{r}
# select data
P300_untrained <- data_untrained %>%
  filter(correct == 1) %>%
  filter(!subjID %in%  exclusion_eeg)

# change the base level of the Belief and Desire condition to be B+ and D+
#TOM$conditionB <- relevel(TOM$conditionB,  'B+')  
#TOM$conditionD <- relevel(TOM$conditionD, 'D+')  

# Set sum contrasts for all variables.
contrasts(P300_untrained$SUBTLEX_frequency_log_cat) <- contr.sum(2)
contrasts(P300_untrained$block)  <- contr.sum(2)

# check contrasts
contrasts(P300_untrained$SUBTLEX_frequency_log_cat)
contrasts(P300_untrained$block)

# center covariates
P300_untrained <- P300_untrained %>%
  mutate(c_SUBTLEX_frequency_log = SUBTLEX_frequency_log - mean(SUBTLEX_frequency_log, na.rm=TRUE))

P300_untrained <- P300_untrained %>%
  mutate(c_FASQUEL_concreteness = FASQUEL_concreteness - mean(FASQUEL_concreteness, na.rm=TRUE))

P300_untrained <- P300_untrained %>%
  mutate(c_FASQUEL_image_agreement = FASQUEL_image_agreement - mean(FASQUEL_image_agreement, na.rm=TRUE))

P300_untrained <- P300_untrained %>%
  mutate(team = team - mean(team, na.rm=TRUE))
```

```{r}
# indicate the maximal effect strucutre (both fixed and random) that is motivated based on design & hypotheses
f <- P300 ~ block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement * c_FASQUEL_concreteness +
     (block*c_SUBTLEX_frequency_log * c_FASQUEL_image_agreement + c_FASQUEL_concreteness | subjID) +
     (block | target_label)

# select the maximal model that still converges
m_P300_untrained <- buildmer(f,data=P300_untrained,buildmerControl=buildmerControl(direction='order', args=list(control=lmerControl(optimizer='bobyqa'))))
summary(m_P300_untrained)

# save winning model
sink(file = "output_stats/LEALCO-EEG_untrained_P300_LMM.txt")
summary(m_P300_untrained)
sink(file = NULL)
```

# Session Information

```{r}
sessionInfo()
```
